### 2015-03-25 paper/paper.tex
bibtex stuff

\documentclass[twoside]{article}

\usepackage{amsmath,amssymb,amsthm} % Mathematical Symbols, styles, etc

% Used to enable use of the defined labeled enunciations. Usage: \begin{definition}text\end{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

% --Optional-- Font and tweaking used in template
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

% Formatting, refs and stuff
\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF

% Fancy lists. Usage: http://lmgtfy.com/?q=latex+paralist
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them

% Abstract customization
\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

% Title customization
\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

% Header and footer customization
\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{T.\ Kemp, T.\ Kerkhoven, J.\ Klein Brinke, T.\ Sonderen: \shorttitle} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

% Bibliography
\usepackage[backend=bibtex]{biblatex}
\bibliography{references.bib}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\articletitle}{The Effects of Preprocessing Methods on Computation Times for Graph Isomorphisms}
\newcommand{\shorttitle}{Preprocessing for Graph Isomorphisms}

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}} % Article title

\author{
\large
\textsc{Tim Kemp, Tim Kerkhoven, Jeroen Klein Brinke, and Tim Sonderen}\\[2mm] % Your names
\normalsize University of Twente \\ % Your institution
\normalsize \href{mailto:t.kerkhoven@student.utwente.nl}{t.kerkhoven@student.utwente.nl}, 
\href{mailto:t.kemp@student.utwente.nl}{t.kemp@student.utwente.nl},\\ \normalsize
\href{mailto:j.klein.brinke@student.utwente.nl}{j.klein.brinke@student.utwente.nl}, \href{mailto:t.sonderen@student.utwente.nl}{t.sonderen@student.utwente.nl}% Your email addresses
}

\date{\today}

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty}
\maketitle % Insert title

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\begin{abstract}

\noindent Abstract here

\end{abstract}

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\begin{multicols}{2} % Two-column layout throughout the main article text

%------------------------------------------------
\section{Introduction}

Introduction here

%------------------------------------------------

\section{Scope \& Objectives}

Scope \& Objectives here

%------------------------------------------------
\section{Methods}

Methods here

%------------------------------------------------
\section{Description of Algorithms}

Description of Algorithms here

%------------------------------------------------
\section{Proof of Correctness}

Proof of Correctness here

%------------------------------------------------
\section{Computational Experiments}

Computational Experiments here

%------------------------------------------------
\section{Results}

Results here

%------------------------------------------------
\section{Conclusions}

Conclusions here

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

% Bibliography - this is intentionally simple in this template
\begin{thebibliography}{99}

\bibitem{Fig2009}
Figueredo, A.~J.\ and Wolf, P.\ S.~A.\ (2009).
Assortative pairing and life history strategy - a cross-cultural study.
\emph{Human Nature \& Arts}, 20:317-330.

\bibitem{Lang2011}
R.\ Langerak  (2011).
How to write a {\tt python} computer program.
\emph{Annals of Improbable Research}, 2:16-27.

\end{thebibliography}

%----------------------------------------------------------------------------------------

\end{multicols}

\end{document}

### 2015-03-25 colorRefinement.py
debug prints weg

@@ -6,7 +6,6 @@ from makegraphs import disjointunion
 from graphIO import *
 
 
-numberOfGraphs = 0
 undecidedGraphs = []
 graphlist = []
 
@@ -170,11 +169,9 @@ def splitColorDict(colordict, g):
 	number = 0
 	partitions = []
 	for i in range(len(subgraphsl)):
-		partitions.append(list(range(number, number+subgraphsl[i])))
+		partitions.append(list(range(number, number + subgraphsl[i])))
 		number += subgraphsl[i]
-	print('partitions  ', partitions)
 
-	#partitions = splitlist(range(len(g.V())), int(len(g.V()) / numberOfGraphs))
 	split = []
 	split2 = []
 	for j in range(numberOfGraphs):
@@ -277,4 +274,4 @@ print(compare("GI_TestInstancesWeek1/crefBM_4_7.grl"))
 # aa = loadgraph("GI_TestInstancesWeek1/hugecographs.grl", readlist=False)
 # print(preprocessing(aa))
 # elapsed_time = time.clock() - start_time
-#print('a: {0:.4f} sec'.format(elapsed_time))
+# print('a: {0:.4f} sec'.format(elapsed_time))

### 2015-03-25 colorRefinement.py
preprocessing

@@ -59,219 +59,227 @@ def refine(g):
 	# initialize
 	colordict = degcolordict(g)
 
-	done = False
-	start_time = time.clock()
-	counter = 0
-	while not done:
-		done = True
-		counter += 1
-		if counter % 100 == 0:
-			print(counter)
-		tempcolordict = dict()
 
-		for key in colordict.keys():
-			nextcolor = max(colordict.keys()) + 1
-			buren = tuple()
-			for value in colordict[key]:
-				nc = sorted(tuple(getNeighbourColors(value)))
-				if len(buren) == 0:
-					buren = nc
+done = False
+start_time = time.clock()
+counter = 0
+while not done:
+    done = True
+    counter += 1
+    if counter % 100 == 0:
+        print(counter)
+    tempcolordict = dict()
 
-				if buren != nc:
-					done = False
-					if nextcolor in tempcolordict:
-						tempcolordict[nextcolor].append(value)
-					else:
-						tempcolordict[nextcolor] = [value]
+    for key in colordict.keys():
+        nextcolor = max(colordict.keys()) + 1
+        buren = tuple()
+        for value in colordict[key]:
+            nc = sorted(tuple(getNeighbourColors(value)))
+            if len(buren) == 0:
+                buren = nc
 
-				else:
-					if key in tempcolordict:
-						tempcolordict[key].append(value)
-					else:
-						tempcolordict[key] = [value]
+            if buren != nc:
+                done = False
+                if nextcolor in tempcolordict:
+                    tempcolordict[nextcolor].append(value)
+                else:
+                    tempcolordict[nextcolor] = [value]
 
-		colordict = tempcolordict.copy()
+            else:
+                if key in tempcolordict:
+                    tempcolordict[key].append(value)
+                else:
+                    tempcolordict[key] = [value]
 
-		for key in colordict.keys():
-			for value in colordict[key]:
-				value.colornum = key
+    colordict = tempcolordict.copy()
 
-	finalcolors = []
-	for node in g.V():
-		finalcolors.append(node.colornum)
+    for key in colordict.keys():
+        for value in colordict[key]:
+            value.colornum = key
 
-	elapsed_time = time.clock() - start_time
-	print('Time: {0:.4f} sec'.format(elapsed_time))
[…]

### 2015-03-25 colorRefinement.py
preprocessing

@@ -55,64 +55,64 @@ def fastrefine(g, startcolor=-1):
 	return colordict
 
 
-def refine(g):
-	# initialize
-	colordict = degcolordict(g)
-
-
-done = False
-start_time = time.clock()
-counter = 0
-while not done:
-    done = True
-    counter += 1
-    if counter % 100 == 0:
-        print(counter)
-    tempcolordict = dict()
-
-    for key in colordict.keys():
-        nextcolor = max(colordict.keys()) + 1
-        buren = tuple()
-        for value in colordict[key]:
-            nc = sorted(tuple(getNeighbourColors(value)))
-            if len(buren) == 0:
-                buren = nc
-
-            if buren != nc:
-                done = False
-                if nextcolor in tempcolordict:
-                    tempcolordict[nextcolor].append(value)
-                else:
-                    tempcolordict[nextcolor] = [value]
-
-            else:
-                if key in tempcolordict:
-                    tempcolordict[key].append(value)
-                else:
-                    tempcolordict[key] = [value]
-
-    colordict = tempcolordict.copy()
-
-    for key in colordict.keys():
-        for value in colordict[key]:
-            value.colornum = key
-
-finalcolors = []
-for node in g.V():
-    finalcolors.append(node.colornum)
-
-elapsed_time = time.clock() - start_time
-print('Time: {0:.4f} sec'.format(elapsed_time))
-# DUS HIER SHIT DOEN MET COLORDICT EN DUBBELE KLEUREN ENZO
-try:
-    result = compareColors(splitColorDict(colordict, g)[0])
-    if len(undecidedGraphs) > 0:
-        print(undecidedGraphs)
-        findDuplicates(splitColorDict(colordict, g)[1])
-    return result
-except:
-    print('its only one graph apparently')
-    return colordict
+# def refine(g):
+# # initialize
+# 	colordict = degcolordict(g)
+#
+#
+# done = False
+# start_time = time.clock()
+# counter = 0
+# while not done:
+#     done = True
+#     counter += 1
+#     if counter % 100 == 0:
+#         print(counter)
+#     tempcolordict = dict()
+#
+#     for key in colordict.keys():
+#         nextcolor = max(colordict.keys()) + 1
+#         buren = tuple()
+#         for value in colordict[key]:
+#             nc = sorted(tuple(getNeighbourColors(value)))
+#             if len(buren) == 0:
+#                 buren = nc
+#
+#             if buren != nc:
[…]

### 2015-03-25 colorRefinement.py
preprocessing

@@ -220,25 +220,6 @@ def gettwins(g):
     return list(falsetwins.values()), list(twins.values()), list(falsetwins.keys()), list(
         twins.keys())  # value zijn twins
 
-def preprocessing2(g):
-    falsetwins, twins, falsetwinsN, twinsN = gettwins(g)
-    removed = []
-    for index in range(len(falsetwins)):
-        for u in falsetwins[index]:
-            for v in falsetwinsN[index]:
-                for i, e in enumerate(g._E):
-                    if (e._tail == u and e._head == v) or (e._tail == v and e._head == u):
-                        g._E.pop(i)
-            removed.append(u._label)
-
-    print('removed:', removed)
-    print('a', g.E())
-    for twin in twins:
-        for i in range(len(twin)):
-            pass
-    return falsetwins, twins
-
-
 def preprocessing(g):
     falsetwins, twins, falsetwinsN, twinsN = gettwins(g)
     deledges = []
@@ -247,18 +228,22 @@ def preprocessing(g):
                         e._tail in twin for twin in twins) or any(e._head in twin for twin in twins):
             deledges.append(i)
     deledges.sort(reverse=True)
-    for index in deledges:
-        g._E.pop(index)
+    for i in deledges:
+        g._E.pop(i)
     delnodes = []
     for i, V in enumerate(g._V):
         if any(V in ftwin for ftwin in falsetwins) or any(V in twin for twin in twins):
             delnodes.append(i)
     delnodes.sort(reverse=True)
-    for index in delnodes:
-        g._V.pop(index)
-    print(g.V())
-
-    return falsetwins, twins
+    for i in delnodes:
+        g._V.pop(i)
+    combined = falsetwinsN + twinsN
+    print(combined)
+    for i, twin in enumerate(falsetwins + twins):
+        g.addvertex(twin[0]._label)
+        for j in combined[i]:
+            g.addedge(twin[0], j)
+    return g
 
 
 def findDuplicates(split2):
@@ -297,9 +282,7 @@ def testpre(graphlisturl):
     start_time = time.clock()
     global graphlist
     graphlist = loadgraph(graphlisturl, readlist=True)
-    result = preprocessing(disjoint())
-    print(result[0])
-    print(result[1])
+    print(preprocessing(disjoint()))
     elapsed_time = time.clock() - start_time
[…]

### 2015-03-26 basicgraphs.py
heeeeeel veel netjes gemaakt en bij gemaakt en gefixed. zit nu met recursion error, jeroen go fix :P

@@ -158,6 +158,12 @@ class graph():
 			self.addvertex()
 		self.enlist = []
 		self.colordict = -1
+		self.vertexreprmap = dict()
+		for v in self._V:
+			self.vertexreprmap[v.__repr__()] = v
+
+	def getvertexbyrepr(self, repr):
+		return self.vertexreprmap[repr]
 
 	def __repr__(self):
 		return 'V=' + str(self._V) + '\nE=' + str(self._E)

### 2015-03-26 colorRefinement.py

@@ -6,30 +6,36 @@ from makegraphs import disjointunion
 from graphIO import *
 
 
-undecidedGraphs = []
-graphlist = []
-
-
-def fastrefine(g, startcolor=-1):
+def fastrefine(g, startcolor=-1, colordict=-1):
 	start_time = time.clock()
-	colordict = degcolordict(g)
+	if colordict is -1:
+		colordict = degcolordict(g)
+
 	if startcolor is -1:
-		queue = [min(colordict.keys())]
+		shortest = min(colordict.keys())
+		for key in colordict.keys():
+			if len(colordict[key]) <= len(colordict[shortest]):
+				shortest = key
+		queue = [shortest]
 	else:
 		queue = [startcolor]
+
 	nextcolor = max(colordict.keys()) + 1
+
 	i = 0
 	while i < len(queue):
 		connectednodes = dict()
-		for node in colordict[queue[i]]:
-			for nb in node.nbs():  # make colordict of neighbours
+		for value in colordict[queue[i]]:
+			for nb in value.nbs():  # make colordict of neighbours
 				if nb.colornum not in connectednodes:
 					connectednodes[nb.colornum] = [nb]
 				elif nb not in connectednodes[nb.colornum]:
 					connectednodes[nb.colornum].append(nb)
 		for key in connectednodes.keys():
 			colordictchanged = False
-			if len(colordict[key]) == len(connectednodes[key]):
+			colordict[key].sort(key=lambda x: x._label)
+			connectednodes[key].sort(key=lambda x: x._label)
+			if colordict[key] == connectednodes[key]:
 				pass
 			elif key not in queue and len(colordict[key]) < len(connectednodes[key]):
 				queue.append(key)
@@ -42,16 +48,14 @@ def fastrefine(g, startcolor=-1):
 				for vertex in connectednodes[key]:
 					vertex.colornum = nextcolor
 				colordict = g.getcolordict()
-				nextcolor = max(colordict.keys()) + 1
+				nextcolor += 1
 		i += 1
-	print('end')
-	print(colordict)
 	elapsed_time = time.clock() - start_time
 	print('Time: {0:.4f} sec'.format(elapsed_time))
-	try:
-		return compareColors(splitColorDict(colordict, g)[0])
-	except:
-		print('its only one graph apparently')
+	# try:
[…]

### 2015-03-27 colorRefinement.py
preprocessing

@@ -48,270 +48,212 @@ def fastrefine(g, startcolor=-1, colordict=-1):
 				for vertex in connectednodes[key]:
 					vertex.colornum = nextcolor
 				colordict = g.getcolordict()
-				nextcolor += 1
+                nextcolor = max(colordict.keys()) + 1
 		i += 1
+    print('end')
+    print(colordict)
 	elapsed_time = time.clock() - start_time
 	print('Time: {0:.4f} sec'.format(elapsed_time))
-	# try:
-	# return compareColors(splitColorDict(colordict, g)[0])
-	# except:
-	# print('its only one graph apparently')
+	try:
+        return compareColors(splitColorDict(colordict, g)[0])
+	except:
+		print('its only one graph apparently')
 	return colordict
 
 
-def refine(g):
-	# initialize
-	colordict = degcolordict(g)
-
-	done = False
-	start_time = time.clock()
-	counter = 0
-	while not done:
-		done = True
-		counter += 1
-		if counter % 100 == 0:
-			print(counter)
-		tempcolordict = dict()
-
-		for key in colordict.keys():
-			nextcolor = max(colordict.keys()) + 1
-			buren = tuple()
-			for value in colordict[key]:
-				nc = sorted(tuple(getNeighbourColors(value)))
-				if len(buren) == 0:
-					buren = nc
-
-				if buren != nc:
-					done = False
-					if nextcolor in tempcolordict:
-						tempcolordict[nextcolor].append(value)
-					else:
-						tempcolordict[nextcolor] = [value]
-
-				else:
-					if key in tempcolordict:
-						tempcolordict[key].append(value)
-					else:
-						tempcolordict[key] = [value]
-
-		colordict = tempcolordict.copy()
-
-		for key in colordict.keys():
-			for value in colordict[key]:
-				value.colornum = key
-
-	finalcolors = []
-	for node in g.V():
-		finalcolors.append(node.colornum)
-
-	elapsed_time = time.clock() - start_time
-	print('Time: {0:.4f} sec'.format(elapsed_time))
-	# DUS HIER SHIT DOEN MET COLORDICT EN DUBBELE KLEUREN ENZO
-	try:
-		result = compareColors(splitColorDict(colordict, g)[0])
-		if len(undecidedGraphs) > 0:
-			print(undecidedGraphs)
-			findDuplicates(splitColorDict(colordict, g)[1])
-		return result
-	except:
-		print('its only one graph apparently')
-		return colordict
[…]

### 2015-03-27 colorRefinement.py
preprocessing

@@ -6,59 +6,59 @@ from makegraphs import disjointunion
 from graphIO import *
 
 
-def fastrefine(g, startcolor=-1, colordict=-1):
-	start_time = time.clock()
-	if colordict is -1:
-		colordict = degcolordict(g)
-
-	if startcolor is -1:
-		shortest = min(colordict.keys())
-		for key in colordict.keys():
-			if len(colordict[key]) <= len(colordict[shortest]):
-				shortest = key
-		queue = [shortest]
-	else:
-		queue = [startcolor]
-
-	nextcolor = max(colordict.keys()) + 1
-
-	i = 0
-	while i < len(queue):
-		connectednodes = dict()
-		for value in colordict[queue[i]]:
-			for nb in value.nbs():  # make colordict of neighbours
-				if nb.colornum not in connectednodes:
-					connectednodes[nb.colornum] = [nb]
-				elif nb not in connectednodes[nb.colornum]:
-					connectednodes[nb.colornum].append(nb)
-		for key in connectednodes.keys():
-			colordictchanged = False
-			colordict[key].sort(key=lambda x: x._label)
-			connectednodes[key].sort(key=lambda x: x._label)
-			if colordict[key] == connectednodes[key]:
-				pass
-			elif key not in queue and len(colordict[key]) < len(connectednodes[key]):
-				queue.append(key)
-				colordictchanged = True
-			else:
-				queue.append(nextcolor)
-				colordictchanged = True
-
-			if colordictchanged:
-				for vertex in connectednodes[key]:
-					vertex.colornum = nextcolor
-				colordict = g.getcolordict()
-                nextcolor = max(colordict.keys()) + 1
-		i += 1
-    print('end')
-    print(colordict)
-	elapsed_time = time.clock() - start_time
-	print('Time: {0:.4f} sec'.format(elapsed_time))
-	try:
-        return compareColors(splitColorDict(colordict, g)[0])
-	except:
-		print('its only one graph apparently')
-	return colordict
+# def fastrefine(g, startcolor=-1, colordict=-1):
+# start_time = time.clock()
+# 	if colordict is -1:
+# 		colordict = degcolordict(g)
+#
+# 	if startcolor is -1:
+# 		shortest = min(colordict.keys())
+# 		for key in colordict.keys():
+# 			if len(colordict[key]) <= len(colordict[shortest]):
+# 				shortest = key
+# 		queue = [shortest]
+# 	else:
[…]

### 2015-03-31 paper/paper.tex
wrote the first two chapters and provided a setup for the third.

@@
 \usepackage{amsmath,amssymb,amsthm} % Mathematical Symbols, styles, etc
+
+\usepackage[utf8]{inputenc} % UTF-8 character encoding stuff
 
@@
 
-Introduction here
+This paper will discuss the effect of several preprocessing methods on the computation time of the graph isomorphism problem.
+This paper will mostly focus on the algorithms and their correctness, in combination with computational experiments and their results.
+
+The graph isomorphism problem is the computational problem of determining whether two finite graphs are isomorphic.
+Besides its practical importance, the graph isomorphism problem is a curiosity in computational complexity theory as it is one of a very small number of problems belonging to NP neither known to be solvable in polynomial time nor NP-complete: it is one of only 12 such problems listed by Garey \& Johnson (1979)\cite{book:garyJohnson1979}, and one of only two of that list whose complexity remains unresolved.
+As of 2008 the best algorithm (Eugene Luks, 1983) has run time $2^{O(\sqrt{n log n})}$ for graphs with \emph{n} vertices.\cite{article:davidJohnson2005}\cite{inproceedings:babaiCodenotti2008}\cite{website:wikiGI}
+
+The preprocessing part are algorithms that look at the graphs before determining whether they are isomorphic with the intent of speeding up the actual process of the determining whether the graphs are isomorphic.
 
@@
 
-Scope \& Objectives here
+The aim of this research paper is to determine whether certain preprocessing methods significantly reduce the time required to check whether two graphs are isomorphic.
+At the core, two cases will be compared: a basic case without preprocessing, and a case with preprocessing.
+
+For this paper, the time complexity of the algorithms will not be discussed or calculated.
+The difference in performance of the cases will be shown from a statistical analysis of computational results.
+
+This paper will give a description of the algorithms used for preproccesing, as well as proof of correctness. The algorithms used to check for isomorphisms will be left out of consideration.
 
@@
 
-Methods here
+TBD - exact setup of experiment - what methods were used to test
+Used to examine validity of the experiment by outsiders, by very precise, give reasons for methods and setup, possibly give alternatives and arguments for them, but describe why we chose the current methods.
 
@@
 Description of Algorithms here
+Don't forget to reference the slides
 
@@
 Computational Experiments here
+Setup good experiments beforehand and test extensively
 
@@
 Results here
+And statistical analysis of the results
 
@@
 Conclusions here 
+Is it faster?
 
@@
 
-% Bibliography - this is intentionally simple in this template
-\begin{thebibliography}{99}
-
-\bibitem{Fig2009}
-Figueredo, A.~J.\ and Wolf, P.\ S.~A.\ (2009).
-Assortative pairing and life history strategy - a cross-cultural study.
-\emph{Human Nature \& Arts}, 20:317-330.
-
-\bibitem{Lang2011}
-R.\ Langerak  (2011).
-How to write a {\tt python} computer program.
-\emph{Annals of Improbable Research}, 2:16-27.
-
-\end{thebibliography}
+\printbibliography
 

### 2015-04-01 colorRefinement.py
Start of countisomorphism

@@ -6,255 +6,317 @@ from makegraphs import disjointunion
 from graphIO import *
 
 
-# def fastrefine(g, startcolor=-1, colordict=-1):
-# start_time = time.clock()
-# 	if colordict is -1:
-# 		colordict = degcolordict(g)
-#
-# 	if startcolor is -1:
-# 		shortest = min(colordict.keys())
-# 		for key in colordict.keys():
-# 			if len(colordict[key]) <= len(colordict[shortest]):
-# 				shortest = key
-# 		queue = [shortest]
-# 	else:
-# 		queue = [startcolor]
-#
-# 	nextcolor = max(colordict.keys()) + 1
-#
-# 	i = 0
-# 	while i < len(queue):
-# 		connectednodes = dict()
-# 		for value in colordict[queue[i]]:
-# 			for nb in value.nbs():  # make colordict of neighbours
-# 				if nb.colornum not in connectednodes:
-# 					connectednodes[nb.colornum] = [nb]
-# 				elif nb not in connectednodes[nb.colornum]:
-# 					connectednodes[nb.colornum].append(nb)
-# 		for key in connectednodes.keys():
-# 			colordictchanged = False
-# 			colordict[key].sort(key=lambda x: x._label)
-# 			connectednodes[key].sort(key=lambda x: x._label)
-# 			if colordict[key] == connectednodes[key]:
-# 				pass
-# 			elif key not in queue and len(colordict[key]) < len(connectednodes[key]):
-# 				queue.append(key)
-# 				colordictchanged = True
-# 			else:
-# 				queue.append(nextcolor)
-# 				colordictchanged = True
-#
-# 			if colordictchanged:
-# 				for vertex in connectednodes[key]:
-# 					vertex.colornum = nextcolor
-# 				colordict = g.getcolordict()
-#                 nextcolor = max(colordict.keys()) + 1
-# 		i += 1
-#     print('end')
-#     print(colordict)
-# 	elapsed_time = time.clock() - start_time
-# 	print('Time: {0:.4f} sec'.format(elapsed_time))
-# 	try:
-#         return compareColors(splitColorDict(colordict, g)[0])
-# 	except:
-# 		print('its only one graph apparently')
-# 	return colordict
+def fastrefine(g, startcolor=-1, colordict=-1):
+	start_time = time.clock()
+	if colordict is -1:
+		colordict = degcolordict(g)
+
+	if startcolor is -1:
+		shortest = min(colordict.keys())
[…]

### 2015-04-01 colorRefinement.py
Start of countisomorphism

@@ -216,7 +216,7 @@ def countIsomorphism(graph):
 					n]  # we'll give the the colors in the colordict the assigned colors
 			newcolor = max(graph.get_colordict().keys()) + 1  # assign a new color
 			# todo: permenantly change colors of nodes.. Instead of resetting them :(
-			# what needs to be done is basically change a nodes color in one graph and one in the other and then use fastrefine.
+			# what needs to be done is basically change a nodes color in one graph and one in the other and then use countIsomorphisms on that.
 			num += countIsomorphism(graph)
 		print(num)
 		return num

### 2015-04-02 colorRefinement.py
Start of countisomorphism

@@ -6,7 +6,7 @@ from makegraphs import disjointunion
 from graphIO import *
 
 
-def fastrefine(g, startcolor=-1, colordict=-1):
+def fastrefine(g, colordict=-1, startcolor=-1):
 	start_time = time.clock()
 	if colordict is -1:
 		colordict = degcolordict(g)
@@ -181,17 +181,23 @@ def compare(graphlisturl=-1, gs=-1):
 			for second in undecided:
 				if second > first:
 					print("First: ", first, ", Second: ", second)
-					countIsomorphism(disjointunion(graphlist[first], graphlist[second]))
+					num = countIsomorphism(disjointunion(graphlist[first], graphlist[second]))
+
 
 	# individualization here
 
 	return colordict
 
 
-def countIsomorphism(graph):
-	colordict = fastrefine(graph)
+def countIsomorphism(graph, hasColordict=False):
+	print("CountIsomorphism bruh!")
+	if hasColordict is False:
+		colordict = fastrefine(graph)
+	else:
+		colordict = fastrefine(graph, hasColordict)
 	isomorphism = True
 	colors = []
+	print("Colordict: ", colordict)
 	for c in colordict.keys():
 		length = len(colordict[c])
 		if length >= 4:  # if there are more than 4 elemts in colordict[c], it means there are duplicates
@@ -207,19 +213,29 @@ def countIsomorphism(graph):
 		nodes = graph.V()
 		anotherDict = dict()
 		for n in nodes:
-			anotherDict[n] = n.colornum  # node and it's color to a dict (Node: color)
-		x = colors[0]  # we'lls tart with the first color
+			anotherDict[n] = n.colornum  # node and its color to a dict (Node: color)
+		onehalf = colors[0:int(len(colors) / 2)]
+		otherhalf = colors[int((len(colors) / 2)):(len(colors))]
+		index = 0
+		x = colors[index]  # we'lls tart with the first color
 		num = 0
-		for y in colors[int(len(colors) / 2)::]:  # get the middle of colors[] (as it skips the first half)
+		for y in otherhalf:  # get the middle of colors[] (as it skips the first half)
 			for n in nodes:
 				graph.getcolordict()[n] = anotherDict[
 					n]  # we'll give the the colors in the colordict the assigned colors
-			newcolor = max(graph.get_colordict().keys()) + 1  # assign a new color
+			newcolor = max(graph.getcolordict().keys()) + 1  # assign a new color
+			colordict[c].remove(x)
[…]

### 2015-04-02 colorRefinement.py
Start of countisomorphism

@@ -219,10 +219,7 @@ def countIsomorphism(graph, hasColordict=False):
 		index = 0
 		x = colors[index]  # we'lls tart with the first color
 		num = 0
-		for y in otherhalf:  # get the middle of colors[] (as it skips the first half)
-			for n in nodes:
-				graph.getcolordict()[n] = anotherDict[
-					n]  # we'll give the the colors in the colordict the assigned colors
+		for y in otherhalf:  # get the middle of colors[] (as it skips the first half)s
 			newcolor = max(graph.getcolordict().keys()) + 1  # assign a new color
 			colordict[c].remove(x)
 			colordict[c].remove(y)

### 2015-04-02 colorRefinement.py
Start of countisomorphism

@@ -210,10 +210,6 @@ def countIsomorphism(graph, hasColordict=False):
 	if isomorphism:
 		return 1
 	else:
-		nodes = graph.V()
-		anotherDict = dict()
-		for n in nodes:
-			anotherDict[n] = n.colornum  # node and its color to a dict (Node: color)
 		onehalf = colors[0:int(len(colors) / 2)]
 		otherhalf = colors[int((len(colors) / 2)):(len(colors))]
 		index = 0

### 2015-04-04 colorRefinement.py
nieuwe dev branch, nieuwe versie van de code. probeer hier preprocessing bij te drukken en dan moet individualization eindelijk af. die is hier nog disabled

@@ -7,7 +7,6 @@ from graphIO import *
 
 
 def fastrefine(g, colordict=-1, startcolor=-1):
-	start_time = time.clock()
 	if colordict is -1:
 		colordict = degcolordict(g)
 
@@ -50,8 +49,6 @@ def fastrefine(g, colordict=-1, startcolor=-1):
 				colordict = g.getcolordict()
 				nextcolor += 1
 		i += 1
-	elapsed_time = time.clock() - start_time
-	print('Time: {0:.4f} sec'.format(elapsed_time))
 	# try:
 	# return compareColors(splitColorDict(colordict, g)[0])
 	# except:
@@ -103,10 +100,6 @@ def refine(g):
 	finalcolors = []
 	for node in g.V():
 		finalcolors.append(node.colornum)
-
-	elapsed_time = time.clock() - start_time
-	print('Time: {0:.4f} sec'.format(elapsed_time))
-	# DUS HIER SHIT DOEN MET COLORDICT EN DUBBELE KLEUREN ENZO
 	try:
 		result = compareColors(splitColorDict(colordict, g)[0])
 		if len(undecidedGraphs) > 0:
@@ -165,7 +158,6 @@ def compare(graphlisturl=-1, gs=-1):
 				if graphcolors[i] == graphcolors[j]:
 					isomorphisms.append([i, j])
 
-	print(undecided)
 	if not undecided:  # status update
 		if isomorphisms:
 			print("Isomorphisms found: ", isomorphisms)
@@ -174,17 +166,15 @@ def compare(graphlisturl=-1, gs=-1):
 		return colordict
 	else:
 		print('Isomorphisms found: ', isomorphisms)
-		print('There are still undecided graphs left, continuing search..')
+		print('There are still undecided graphs left: ', undecided)
+		print('Continuing search...')
 
-	if len(undecided) > 0:
-		for first in undecided:
-			for second in undecided:
-				if second > first:
-					print("First: ", first, ", Second: ", second)
-					num = countIsomorphism(disjointunion(graphlist[first], graphlist[second]))
-
-
-	# individualization here
+	# if len(undecided) > 0:  #########################################uncomment this to activate individualization again
+	# 	for first in undecided:
+	# 		for second in undecided:
+	# 			if second > first:
+	# 				print("First: ", first, ", Second: ", second)
+	# 				num = countIsomorphism(disjointunion(graphlist[first], graphlist[second]))
 
 	return colordict
 

### 2015-04-04 colorRefinement.py
preprocessing ingevoegd

@@ -7,220 +7,220 @@ from graphIO import *
 
 
 def fastrefine(g, colordict=-1, startcolor=-1):
-	if colordict is -1:
-		colordict = degcolordict(g)
+    if colordict is -1:
+        colordict = degcolordict(g)
 
-	if startcolor is -1:
-		shortest = min(colordict.keys())
-		for key in colordict.keys():
-			if len(colordict[key]) <= len(colordict[shortest]):
-				shortest = key
-		queue = [shortest]
-	else:
-		queue = [startcolor]
+    if startcolor is -1:
+        shortest = min(colordict.keys())
+        for key in colordict.keys():
+            if len(colordict[key]) <= len(colordict[shortest]):
+                shortest = key
+        queue = [shortest]
+    else:
+        queue = [startcolor]
 
-	nextcolor = max(colordict.keys()) + 1
+    nextcolor = max(colordict.keys()) + 1
 
-	i = 0
-	while i < len(queue):
-		connectednodes = dict()
-		for value in colordict[queue[i]]:
-			for nb in value.nbs():  # make colordict of neighbours
-				if nb.colornum not in connectednodes:
-					connectednodes[nb.colornum] = [nb]
-				elif nb not in connectednodes[nb.colornum]:
-					connectednodes[nb.colornum].append(nb)
-		for key in connectednodes.keys():
-			colordictchanged = False
-			colordict[key].sort(key=lambda x: x._label)
-			connectednodes[key].sort(key=lambda x: x._label)
-			if colordict[key] == connectednodes[key]:
-				pass
-			elif key not in queue and len(colordict[key]) < len(connectednodes[key]):
-				queue.append(key)
-				colordictchanged = True
-			else:
-				queue.append(nextcolor)
-				colordictchanged = True
+    i = 0
+    while i < len(queue):
+        connectednodes = dict()
+        for value in colordict[queue[i]]:
+            for nb in value.nbs():  # make colordict of neighbours
+                if nb.colornum not in connectednodes:
+                    connectednodes[nb.colornum] = [nb]
+                elif nb not in connectednodes[nb.colornum]:
+                    connectednodes[nb.colornum].append(nb)
+        for key in connectednodes.keys():
+            colordictchanged = False
+            colordict[key].sort(key=lambda x: x._label)
+            connectednodes[key].sort(key=lambda x: x._label)
+            if colordict[key] == connectednodes[key]:
+                pass
[…]

### 2015-04-04 basicgraphs.py
preprocessing ingevoegd

@@ -15,121 +15,131 @@ unsafe = False
 
 
 class GraphError(Exception):
-	def __init__(self, message):
-		self.mess = message
+    def __init__(self, message):
+        self.mess = message
 
-	def __str__(self):
-		return self.mess
+    def __str__(self):
+        return self.mess
 
 
 class vertex():
-	"""
+    """
     Vertex objects have an attribute <_graph> pointing to the graph they are part of,
     and an attribute <_label> which can be anything: it is not used for any methods,
     except for __repr__.
-    """
-	colornum = None
+ """
+    colornum = None
+    twin = False
+    twinsize = None
+    nbl = -1
+    incl = -1
 
-	nbl = -1
-	incl = -1
-
-	def __init__(self, graph, label=0):
-		"""
+    def __init__(self, graph, label=0):
+        """
         Creates a vertex, part of <graph>, with optional label <label>.
         (Labels of different vertices may be chosen the same; this does
         not influence correctness of the methods, but will make the string
         representation of the graph ambiguous.)
         """
-		self._graph = graph
-		self._label = label
+        self._graph = graph
+        self._label = label
 
-	def __repr__(self):
-		return str(self._label)
+    def __repr__(self):
+        return str(self._label)
 
-	def adj(self, other):
-		"""
+    def adj(self, other):
+        """
         Returns True iff vertex <self> is adjacent to <other> vertex.
         """
-		return self._graph.adj(self, other)
+        return self._graph.adj(self, other)
 
-	def inclist(self):
-		"""
+    def inclist(self):
+        """
         Returns the list of edges incident with vertex <self>.
         """
-		if not self._graph.enlist:
-			self._graph.makeinclist()
-		return self._graph.enlist[self]
+        if not self._graph.enlist:
+            self._graph.makeinclist()
+        return self._graph.enlist[self]
 
-	def nbs(self):
-		"""
+    def nbs(self):
+        """
         Returns the list of neighbors of vertex <self>.
         In case of parallel edges: duplicates are not removed from this list!
         """
-		if self.nbl == -1:
-			self.nbl = []
-			for e in self.inclist():
-				self.nbl.append(e.otherend(self))
-		return self.nbl
+        if self.nbl == -1:
+            self.nbl = []
+            for e in self.inclist():
+                self.nbl.append(e.otherend(self))
+        return self.nbl
 
-	def deg(self):
-		"""
+
+    def fastnbs(self):
+        """
[…]

### 2015-04-04 colorRefinement.py

@@ -6,9 +6,11 @@ from makegraphs import disjointunion
 from graphIO import *
 
 
-def fastrefine(g, colordict=-1, startcolor=-1):
-    if colordict is -1:
+def fastrefine(g, colordict=-1, startcolor=-1, preproc=False):
+    if colordict is -1 and not preproc:
         colordict = degcolordict(g)
+    elif colordict is -1 and preproc:
+        colordict = preproccolordict(g)
 
     if startcolor is -1:
         shortest = min(colordict.keys())
@@ -122,6 +124,20 @@ def degcolordict(g):
     return colordict
 
 
+def preproccolordict(g):
+    colordict = {}  # dictionary with key=c and value=vertex array
+    for v in g.V():
+        if not v.twin:
+            v.colornum = v.deg()
+        else:
+            v.colornum = -v.twinsize
+        if v.colornum not in colordict:
+            colordict[v.colornum] = [v]
+        else:
+            colordict[v.colornum].append(v)
+    return colordict
+
+
 def getNeighbourColors(v):
     colors = []
     for i in v.nbs():
@@ -129,7 +145,7 @@ def getNeighbourColors(v):
     return colors
 
 
-def compare(graphlisturl=-1, gs=-1):
+def compare(graphlisturl=-1, gs=-1, preproc=False):
     assert graphlisturl != -1 or gs != -1
 
     if gs is -1:
@@ -144,8 +160,10 @@ def compare(graphlisturl=-1, gs=-1):
         g = disjointunion(g, h)
         subgraphlist.append(len(h.V()))
     g.subgraphs = subgraphlist
-
-    colordict = fastrefine(g)
+    if preproc:
+        colordict = fastrefine(g, preproc=True)
+    else:
+        colordict = fastrefine(g)
     graphcolors = splitColorDict(colordict, g)[0]
 
     isomorphisms = []
@@ -343,8 +361,12 @@ def preprocessing(g):
         for i in delnodes:
             g._V.pop(i)
         combined = falsetwinsN + twinsN
-        for i, twin in enumerate(falsetwins + twins):
-            g.addvertex(twin[0]._label)
+        mx = 0
+        for i, twin in enumerate(falsetwins):
+            g.addvertex(twin[0]._label, True, len(twin))
+            mx = max(mx, len(twin))
+        for i, twin in enumerate(twins):
[…]

### 2015-04-04 colorRefinement.py
wat prints toegevoegd om error te vinden

@@ -157,6 +157,9 @@ def compare(graphlisturl=-1, gs=-1, preproc=False):
     subgraphlist.append(len(g.V()))
     for i in range(1, len(graphlist)):  # make one big graph from the graphlist
         h = graphlist[i]
+        print(i)
+        print(h)
+        print(g)
         g = disjointunion(g, h)
         subgraphlist.append(len(h.V()))
     g.subgraphs = subgraphlist

### 2015-04-04 basicgraphs.py
een error ingewisseld voor een andere :)

@@ -57,8 +57,10 @@ class vertex():
         """
         Returns the list of edges incident with vertex <self>.
         """
+        print('enlist', self._graph.enlist)
         if not self._graph.enlist:
             self._graph.makeinclist()
+        print(self._graph.enlist)
         return self._graph.enlist[self]
 
     def nbs(self):
@@ -85,7 +87,7 @@ class vertex():
         """
         Returns the degree of vertex <self>.
         """
-        return len(self.inclist())
+        return len(self._graph.nbsdict[self])
 
 
 class edge():

### 2015-04-04 colorRefinement.py

@@ -126,8 +126,10 @@ def degcolordict(g):
 
 def preproccolordict(g):
     colordict = {}  # dictionary with key=c and value=vertex array
+    print('V:', g.V())
     for v in g.V():
         if not v.twin:
+            print('nbs', list(g.nbsdict.keys()))
             v.colornum = v.deg()
         else:
             v.colornum = -v.twinsize
@@ -157,11 +159,9 @@ def compare(graphlisturl=-1, gs=-1, preproc=False):
     subgraphlist.append(len(g.V()))
     for i in range(1, len(graphlist)):  # make one big graph from the graphlist
         h = graphlist[i]
-        print(i)
-        print(h)
-        print(g)
         g = disjointunion(g, h)
         subgraphlist.append(len(h.V()))
+    g.makenbsdict()
     g.subgraphs = subgraphlist
     if preproc:
         colordict = fastrefine(g, preproc=True)
@@ -388,7 +388,8 @@ def testpre(graphlisturl):
     nfalsetwins, ntwins = [None] * ngraphs, [None] * ngraphs
     for i in range(ngraphs):
         graphlist[0][i], nfalsetwins[i], ntwins[i] = preprocessing(graphlist[0][i])
-        print(graphlist[0][i])
+        # print(graphlist[0][i])
+        #isgraph(graphlist[0][i])
     print(nfalsetwins, ntwins)
     elapsed_time = time.clock() - start_time
     print('total time: {0:.4f} sec'.format(elapsed_time))
@@ -399,6 +400,13 @@ def individualizationRefinement():
     return 0
 
 
+def isgraph(g):
+    print('V:', g.V())
+    for edge in g.E():
+        if edge.head() not in g.V() or edge.tail() not in g.V():
+            print('error: ', edge)
+
+
 # print(fastrefine(loadgraph("GI_TestInstancesWeek1/crefBM_4_16.grl", readlist=False)))
 # compare("GI_TestInstancesWeek1/crefBM_4_9.grl")
 # print(compare("GI_TestInstancesWeek1/threepaths10240.gr"))
@@ -406,3 +414,5 @@ def individualizationRefinement():
 
 #print(compare("GI_TestInstancesWeek1/hugecographs.grl"))
 print(testpre("GI_TestInstancesWeek1/hugecographs.grl"))
+
+

### 2015-04-04 makegraphs.py

@@ -1,5 +1,6 @@
 # DW 2 practicum, Ex1 solution
 from builtins import print
+
 from basicgraphs import graph
 
 
@@ -29,9 +30,10 @@ def disjointunion(G, H):
 	vmap = {}
 	K = graph()
 	for v in G.V() + H.V():
-		vmap[v] = K.addvertex()
+        vmap[v._label] = K.addvertex()
+    print(vmap)
 	for e in G.E() + H.E():
-		K.addedge(vmap[e.tail()], vmap[e.head()])
+        K.addedge(vmap[e.tail()._label], vmap[e.head()._label])
 	return K
 
 

### 2015-04-04 basicgraphs.py
werkt nog niet maar wel errorvrij :) en iets sneller!

@@ -57,10 +57,8 @@ class vertex():
         """
         Returns the list of edges incident with vertex <self>.
         """
-        print('enlist', self._graph.enlist)
         if not self._graph.enlist:
             self._graph.makeinclist()
-        print(self._graph.enlist)
         return self._graph.enlist[self]
 
     def nbs(self):
@@ -87,7 +85,11 @@ class vertex():
         """
         Returns the degree of vertex <self>.
         """
-        return len(self._graph.nbsdict[self])
+        try:
+            deg = len(self._graph.nbsdict[self])
+        except KeyError:
+            deg = 0
+        return deg
 
 
 class edge():

### 2015-04-04 colorRefinement.py

@@ -22,7 +22,6 @@ def fastrefine(g, colordict=-1, startcolor=-1, preproc=False):
         queue = [startcolor]
 
     nextcolor = max(colordict.keys()) + 1
-
     i = 0
     while i < len(queue):
         connectednodes = dict()
@@ -126,10 +125,8 @@ def degcolordict(g):
 
 def preproccolordict(g):
     colordict = {}  # dictionary with key=c and value=vertex array
-    print('V:', g.V())
     for v in g.V():
         if not v.twin:
-            print('nbs', list(g.nbsdict.keys()))
             v.colornum = v.deg()
         else:
             v.colornum = -v.twinsize
@@ -161,7 +158,8 @@ def compare(graphlisturl=-1, gs=-1, preproc=False):
         h = graphlist[i]
         g = disjointunion(g, h)
         subgraphlist.append(len(h.V()))
-    g.makenbsdict()
+    g.makenbsdict()  # update nbs omdat er een nieuwe graph is
+    g.makeinclist()
     g.subgraphs = subgraphlist
     if preproc:
         colordict = fastrefine(g, preproc=True)
@@ -381,7 +379,6 @@ def preprocessing(g):
 
 
 def testpre(graphlisturl):
-    start_time = time.clock()
     global graphlist
     graphlist = loadgraph(graphlisturl, readlist=True)
     ngraphs = len(graphlist[0])
@@ -390,9 +387,8 @@ def testpre(graphlisturl):
         graphlist[0][i], nfalsetwins[i], ntwins[i] = preprocessing(graphlist[0][i])
         # print(graphlist[0][i])
         #isgraph(graphlist[0][i])
-    print(nfalsetwins, ntwins)
-    elapsed_time = time.clock() - start_time
-    print('total time: {0:.4f} sec'.format(elapsed_time))
+    print('number of twins:', nfalsetwins, ntwins)
+
     return compare(gs=graphlist[0], preproc=True)
 
 
@@ -400,19 +396,18 @@ def individualizationRefinement():
     return 0
 
 
-def isgraph(g):
-    print('V:', g.V())
-    for edge in g.E():
-        if edge.head() not in g.V() or edge.tail() not in g.V():
-            print('error: ', edge)
-
-
 # print(fastrefine(loadgraph("GI_TestInstancesWeek1/crefBM_4_16.grl", readlist=False)))
[…]

### 2015-04-04 makegraphs.py

@@ -5,43 +5,42 @@ from basicgraphs import graph
 
 
 def path(n):
-	P = graph(n)
-	for i in range(n - 1):
-		P.addedge(P[i], P[i + 1])
-	return P
+    P = graph(n)
+    for i in range(n - 1):
+        P.addedge(P[i], P[i + 1])
+    return P
 
 
 def cycle(n):
-	C = graph(n)
-	for i in range(n):
-		C.addedge(C[i], C[(i + 1) % n])
-	return C
+    C = graph(n)
+    for i in range(n):
+        C.addedge(C[i], C[(i + 1) % n])
+    return C
 
 
 def complete(n):
-	K = graph(n)
-	for i in range(n - 1):
-		for j in range(i + 1, n):
-			K.addedge(K[i], K[j])
-	return K
+    K = graph(n)
+    for i in range(n - 1):
+        for j in range(i + 1, n):
+            K.addedge(K[i], K[j])
+    return K
 
 
 def disjointunion(G, H):
-	vmap = {}
-	K = graph()
-	for v in G.V() + H.V():
+    vmap = {}
+    K = graph()
+    for v in G.V() + H.V():
         vmap[v._label] = K.addvertex()
-    print(vmap)
-	for e in G.E() + H.E():
+    for e in G.E() + H.E():
         K.addedge(vmap[e.tail()._label], vmap[e.head()._label])
-	return K
+    return K
 
 
 if __name__ == "__main__":
-	P = path(5)
-	C = cycle(5)
-	K = complete(4)
-	print(P)
-	print(C)
-	print(K)
-	print(disjointunion(disjointunion(P, C), K))
+    P = path(5)
+    C = cycle(5)
+    K = complete(4)
+    print(P)
+    print(C)
+    print(K)
+    print(disjointunion(disjointunion(P, C), K))

### 2015-04-05 colorRefinement.py
stuff, werkt niet met torus24

@@ -9,7 +9,10 @@ from graphIO import *
 def fastrefine(g, colordict=-1, startcolor=-1):
 	start_time = time.clock()
 	if colordict is -1:
-		colordict = degcolordict(g)
+		if g.colordict == -1:
+			colordict = degcolordict(g)
+		else:
+			colordict = g.colordict
 
 	if startcolor is -1:
 		shortest = min(colordict.keys())
@@ -31,6 +34,7 @@ def fastrefine(g, colordict=-1, startcolor=-1):
 					connectednodes[nb.colornum] = [nb]
 				elif nb not in connectednodes[nb.colornum]:
 					connectednodes[nb.colornum].append(nb)
+
 		for key in connectednodes.keys():
 			colordictchanged = False
 			colordict[key].sort(key=lambda x: x._label)
@@ -181,7 +185,8 @@ def compare(graphlisturl=-1, gs=-1):
 			for second in undecided:
 				if second > first:
 					print("First: ", first, ", Second: ", second)
-					num = countIsomorphism(disjointunion(graphlist[first], graphlist[second]))
+					tempgraph = disjointunion(graphlist[first], graphlist[second])
+					num = countIsomorphism(tempgraph, fastrefine(tempgraph))
 
 
 	# individualization here
@@ -210,6 +215,7 @@ def countIsomorphism(graph, hasColordict=False):
 	if isomorphism:
 		return 1
 	else:
+		print('pindas')
 		onehalf = colors[0:int(len(colors) / 2)]
 		otherhalf = colors[int((len(colors) / 2)):(len(colors))]
 		index = 0
@@ -228,6 +234,7 @@ def countIsomorphism(graph, hasColordict=False):
 			colordict[c].append(y)
 			# todo: permenantly change colors of nodes.. Instead of resetting them :(
 			# what needs to be done is basically change a nodes color in one graph and one in the other and then use countIsomorphisms on that.
+	print('num is ', num)
 	return num
 
 	return 0
@@ -361,7 +368,8 @@ def individualizationRefinement():
 
 
 # print(fastrefine(loadgraph("GI_TestInstancesWeek1/crefBM_4_16.grl", readlist=False)))
-compare("GI_TestInstancesWeek1/crefBM_4_9.grl")
+compare("GI_TestInstancesWeek1/torus24.grl")
+#compare("GI_TestInstancesWeek1/crefBM_4_16.grl")
 # print(compare("GI_TestInstancesWeek1/threepaths10240.gr"))
 
 

### 2015-04-05 basicgraphs.py
jaaa t word beter :D 4_7 kan ie nu oplossen, taurus24 gaat nog wel stuk

@@ -178,7 +178,8 @@ class graph():
 		self.colordict = colordict0
 
 	def getcolordict(self):
-		self.generatecolordict()
+		if self.colordict == -1:
+			self.generatecolordict()
 		return self.colordict
 
 	def makeinclist(self):

### 2015-04-05 colorRefinement.py

@@ -6,14 +6,15 @@ from makegraphs import disjointunion
 from graphIO import *
 
 
-def fastrefine(g, colordict=-1, startcolor=-1):
+def fastrefine(g, colordictarg=-1, startcolor=-1):
 	start_time = time.clock()
-	if colordict is -1:
+	if colordictarg is -1:
 		if g.colordict == -1:
 			colordict = degcolordict(g)
 		else:
 			colordict = g.colordict
-
+	else:
+		colordict = colordictarg
 	if startcolor is -1:
 		shortest = min(colordict.keys())
 		for key in colordict.keys():
@@ -23,6 +24,7 @@ def fastrefine(g, colordict=-1, startcolor=-1):
 	else:
 		queue = [startcolor]
 
+	applycolors(colordict)
 	nextcolor = max(colordict.keys()) + 1
 
 	i = 0
@@ -51,6 +53,7 @@ def fastrefine(g, colordict=-1, startcolor=-1):
 			if colordictchanged:
 				for vertex in connectednodes[key]:
 					vertex.colornum = nextcolor
+				g.generatecolordict()
 				colordict = g.getcolordict()
 				nextcolor += 1
 		i += 1
@@ -187,7 +190,10 @@ def compare(graphlisturl=-1, gs=-1):
 					print("First: ", first, ", Second: ", second)
 					tempgraph = disjointunion(graphlist[first], graphlist[second])
 					num = countIsomorphism(tempgraph, fastrefine(tempgraph))
+					if num > 0:
+						isomorphisms.append([first,second])
 
+	print('Search ended; Isomorphisms found: ', isomorphisms)
 
 	# individualization here
 
@@ -202,36 +208,41 @@ def countIsomorphism(graph, hasColordict=False):
 		colordict = fastrefine(graph, hasColordict)
 	isomorphism = True
 	colors = []
+	cvar = -1
 	print("Colordict: ", colordict)
 	for c in colordict.keys():
 		length = len(colordict[c])
+		print('length is ', length)
 		if length >= 4:  # if there are more than 4 elemts in colordict[c], it means there are duplicates
 			colorlength = len(colors)
 			if colorlength == 0 or length <= colorlength:
 				colors = colordict[c]  # add these to colors.
+				cvar = c
 				isomorphism = False  # meaning we found no isomorphism again
[…]

### 2015-04-06 colorRefinement.py
6_15 kan ie nu ook, vervelend dat er steeds maar 1 meer kan xD hij moet torus24 gwn op kunnen lossen

@@ -39,7 +39,10 @@ def fastrefine(g, colordictarg=-1, startcolor=-1):
 
 		for key in connectednodes.keys():
 			colordictchanged = False
-			colordict[key].sort(key=lambda x: x._label)
+			try:
+				colordict[key].sort(key=lambda x: x._label)
+			except:
+				print('colordict is ', colordict, '  -- connectednodes is ', connectednodes)
 			connectednodes[key].sort(key=lambda x: x._label)
 			if colordict[key] == connectednodes[key]:
 				pass
@@ -191,7 +194,7 @@ def compare(graphlisturl=-1, gs=-1):
 					tempgraph = disjointunion(graphlist[first], graphlist[second])
 					num = countIsomorphism(tempgraph, fastrefine(tempgraph))
 					if num > 0:
-						isomorphisms.append([first,second])
+						isomorphisms.append([first,second, num])
 
 	print('Search ended; Isomorphisms found: ', isomorphisms)
 
@@ -209,10 +212,8 @@ def countIsomorphism(graph, hasColordict=False):
 	isomorphism = True
 	colors = []
 	cvar = -1
-	print("Colordict: ", colordict)
 	for c in colordict.keys():
 		length = len(colordict[c])
-		print('length is ', length)
 		if length >= 4:  # if there are more than 4 elemts in colordict[c], it means there are duplicates
 			colorlength = len(colors)
 			if colorlength == 0 or length <= colorlength:
@@ -226,21 +227,23 @@ def countIsomorphism(graph, hasColordict=False):
 	else:
 		onehalf = colors[0:int(len(colors) / 2)]
 		otherhalf = colors[int((len(colors) / 2)):(len(colors))]
-		print('otherhalf', otherhalf)
 		index = 0
 		x = colors[index]  # we'lls tart with the first color
 		num = 0
 		for y in otherhalf:  # get the middle of colors[] (as it skips the first half)s
-			print('y is ', y)
 			newcolor = max(graph.getcolordict().keys()) + 1  # assign a new color
-			print('x is ', x, ' -- colordict[c] is ', colordict[cvar], ' -- colors is ', colors)
+			print('######', newcolor)
 			colordict[cvar].remove(x)
 			colordict[cvar].remove(y)
 			colordict[newcolor] = [x]
 			colordict[newcolor].append(y)
-			print("Print colordict: ", colordict)
[…]

### 2015-04-06 basicgraphs.py
In ieder geval fout opgelost :)

@@ -264,6 +264,12 @@ class graph():
         self.enlist = []
         return u
 
+    def addvertexobject(self, vobject):
+        self._V.append(vobject)
+        self.enlist = []
+        return vobject
+
+
     def addedge(self, tail, head):
         """
         Add an edge to the graph between <tail> and <head>.

### 2015-04-06 colorRefinement.py

@@ -341,6 +341,44 @@ def gettwins(g):
         twins.keys())  # value zijn twins
 
 
+# def preprocessingold(g):
+# falsetwins, twins, falsetwinsN, twinsN = gettwins(g)
+#     lftwins = len(falsetwins)
+#     ltwins = len(twins)
+#     if lftwins != 0 or ltwins != 0:
+#         deledges = []
+#         for i, e in enumerate(g._E):
+#             if any(e._tail in ftwin for ftwin in falsetwins) or any(e._head in ftwin for ftwin in falsetwins) or any(
+#                             e._tail in twin for twin in twins) or any(e._head in twin for twin in twins):
+#                 deledges.append(i)
+#         deledges.sort(reverse=True)
+#         for i in deledges:
+#             g._E.pop(i)
+#         delnodes = []
+#         for i, V in enumerate(g._V):
+#             if any(V in ftwin for ftwin in falsetwins) or any(V in twin for twin in twins):
+#                 delnodes.append(i)
+#         delnodes.sort(reverse=True)
+#         for i in delnodes:
+#             g._V.pop(i)
+#         #Alles opnieuw aanmaken
+#         combined = falsetwinsN + twinsN
+#         mx = 0
+#         for i, twin in enumerate(falsetwins):
+#             g.addvertex(twin[0]._label, True, len(twin))
+#             mx = max(mx, len(twin))
+#         for i, twin in enumerate(twins):
+#             g.addvertex(twin[0]._label, True, mx + len(twin))
+#         labels = [l._label for l in g.V()]
+#         for i, twin in enumerate(falsetwins + twins):
+#             for j in combined[i]:
+#                 if j._label in labels and twin[0] != j and not g.findedge(twin[0],
+#                                                                           j):  # Geen loop en geen edges dubbel omgedraaid
+#                     g.addedge(twin[0], j)
+#         g._V.sort(key=lambda x: x._label)
+#         print(twins,falsetwins)
+#     return g, lftwins, ltwins
+
 def preprocessing(g):
     falsetwins, twins, falsetwinsN, twinsN = gettwins(g)
     lftwins = len(falsetwins)
@@ -361,18 +399,18 @@ def preprocessing(g):
         delnodes.sort(reverse=True)
         for i in delnodes:
             g._V.pop(i)
+        # Alles opnieuw aanmaken
[…]

### 2015-04-06 graphIO.py

@@ -222,6 +222,8 @@ def writeDOT(G, filename, directed=False):
 		if hasattr(v, 'colortext'):
 			options += 'color="' + v.colortext + '",'
 		elif hasattr(v, 'colornum'):
+            if v.colornum is None:
+                v.colornum = -10000
 			options += 'color=' + str(v.colornum % numcolors + 1) + ', colorscheme=' + defaultcolorscheme + ','
 			if v.colornum >= numcolors:
 				options += 'style=filled,fillcolor=' + str(v.colornum // numcolors + 1) + ','

### 2015-04-06 basicgraphs.py
stuff

@@ -163,6 +163,9 @@ class graph():
 			self.vertexreprmap[v.__repr__()] = v
 
 	def getvertexbyrepr(self, repr):
+		if not self.vertexreprmap:
+			for v in self._V:
+				self.vertexreprmap[v.__repr__()] = v
 		return self.vertexreprmap[repr]
 
 	def __repr__(self):

### 2015-04-06 colorRefinement.py

@@ -1,6 +1,7 @@
 __author__ = 'Tim (& [Jeroen])'
 
 import time
+import copy
 
 from makegraphs import disjointunion
 from graphIO import *
@@ -39,10 +40,7 @@ def fastrefine(g, colordictarg=-1, startcolor=-1):
 
 		for key in connectednodes.keys():
 			colordictchanged = False
-			try:
-				colordict[key].sort(key=lambda x: x._label)
-			except:
-				print('colordict is ', colordict, '  -- connectednodes is ', connectednodes)
+			colordict[key].sort(key=lambda x: x._label)
 			connectednodes[key].sort(key=lambda x: x._label)
 			if colordict[key] == connectednodes[key]:
 				pass
@@ -60,8 +58,6 @@ def fastrefine(g, colordictarg=-1, startcolor=-1):
 				colordict = g.getcolordict()
 				nextcolor += 1
 		i += 1
-	elapsed_time = time.clock() - start_time
-	print('Time: {0:.4f} sec'.format(elapsed_time))
 	# try:
 	# return compareColors(splitColorDict(colordict, g)[0])
 	# except:
@@ -204,7 +200,7 @@ def compare(graphlisturl=-1, gs=-1):
 
 
 def countIsomorphism(graph, hasColordict=False):
-	print("CountIsomorphism bruh!")
+	#print("CountIsomorphism bruh!")
 	if hasColordict is False:
 		colordict = fastrefine(graph)
 	else:
@@ -232,23 +228,28 @@ def countIsomorphism(graph, hasColordict=False):
 		num = 0
 		for y in otherhalf:  # get the middle of colors[] (as it skips the first half)s
 			newcolor = max(graph.getcolordict().keys()) + 1  # assign a new color
-			print('######', newcolor)
-			colordict[cvar].remove(x)
-			colordict[cvar].remove(y)
-			colordict[newcolor] = [x]
-			colordict[newcolor].append(y)
-			print('colordict before ', colordict)
+			colordict2 = copy.deepcopy(colordict)
+			print(colordict2, x)
+			x2 = graph.getvertexbyrepr(str(x._label))
+			y2 = graph.getvertexbyrepr(str(y._label))
+			colordict2[cvar].remove(x2)
+			colordict2[cvar].remove(y2)
+			colordict2[newcolor] = [x2]
+			colordict2[newcolor].append(y2)
 			num += countIsomorphism(graph, colordict)
-			print('colordict after ', colordict)
[…]

### 2015-04-06 basicgraphs.py
preproc klopt, implementatie niet

@@ -264,7 +264,9 @@ class graph():
         self.enlist = []
         return u
 
-    def addvertexobject(self, vobject):
+    def addvertexobject(self, vobject, twin=False, twinsize=None):
+        vobject.twin = twin
+        vobject.twinsize = twinsize
         self._V.append(vobject)
         self.enlist = []
         return vobject

### 2015-04-06 colorRefinement.py

@@ -128,12 +128,11 @@ def preproccolordict(g):
     for v in g.V():
         if not v.twin:
             v.colornum = v.deg()
-        else:
-            v.colornum = -v.twinsize
         if v.colornum not in colordict:
             colordict[v.colornum] = [v]
         else:
             colordict[v.colornum].append(v)
+    print('dict', colordict)
     return colordict
 
 
@@ -341,44 +340,6 @@ def gettwins(g):
         twins.keys())  # value zijn twins
 
 
-# def preprocessingold(g):
-# falsetwins, twins, falsetwinsN, twinsN = gettwins(g)
-#     lftwins = len(falsetwins)
-#     ltwins = len(twins)
-#     if lftwins != 0 or ltwins != 0:
-#         deledges = []
-#         for i, e in enumerate(g._E):
-#             if any(e._tail in ftwin for ftwin in falsetwins) or any(e._head in ftwin for ftwin in falsetwins) or any(
-#                             e._tail in twin for twin in twins) or any(e._head in twin for twin in twins):
-#                 deledges.append(i)
-#         deledges.sort(reverse=True)
-#         for i in deledges:
-#             g._E.pop(i)
-#         delnodes = []
-#         for i, V in enumerate(g._V):
-#             if any(V in ftwin for ftwin in falsetwins) or any(V in twin for twin in twins):
-#                 delnodes.append(i)
-#         delnodes.sort(reverse=True)
-#         for i in delnodes:
-#             g._V.pop(i)
-#         #Alles opnieuw aanmaken
-#         combined = falsetwinsN + twinsN
-#         mx = 0
-#         for i, twin in enumerate(falsetwins):
-#             g.addvertex(twin[0]._label, True, len(twin))
-#             mx = max(mx, len(twin))
-#         for i, twin in enumerate(twins):
-#             g.addvertex(twin[0]._label, True, mx + len(twin))
-#         labels = [l._label for l in g.V()]
-#         for i, twin in enumerate(falsetwins + twins):
-#             for j in combined[i]:
-#                 if j._label in labels and twin[0] != j and not g.findedge(twin[0],
-#                                                                           j):  # Geen loop en geen edges dubbel omgedraaid
-#                     g.addedge(twin[0], j)
-#         g._V.sort(key=lambda x: x._label)
-#         print(twins,falsetwins)
[…]

### 2015-04-06 graphIO.py

@@ -223,7 +223,7 @@ def writeDOT(G, filename, directed=False):
 			options += 'color="' + v.colortext + '",'
 		elif hasattr(v, 'colornum'):
             if v.colornum is None:
-                v.colornum = -10000
+                v.colornum = -100
 			options += 'color=' + str(v.colornum % numcolors + 1) + ', colorscheme=' + defaultcolorscheme + ','
 			if v.colornum >= numcolors:
 				options += 'style=filled,fillcolor=' + str(v.colornum // numcolors + 1) + ','

### 2015-04-06 colorRefinement.py
fixed :DD

@@ -8,7 +8,6 @@ from graphIO import *
 
 
 def fastrefine(g, colordictarg=-1, startcolor=-1):
-	start_time = time.clock()
 	if colordictarg is -1:
 		if g.colordict == -1:
 			colordict = degcolordict(g)
@@ -58,10 +57,6 @@ def fastrefine(g, colordictarg=-1, startcolor=-1):
 				colordict = g.getcolordict()
 				nextcolor += 1
 		i += 1
-	# try:
-	# return compareColors(splitColorDict(colordict, g)[0])
-	# except:
-	# print('its only one graph apparently')
 	return colordict
 
 
@@ -70,7 +65,6 @@ def refine(g):
 	colordict = degcolordict(g)
 
 	done = False
-	start_time = time.clock()
 	counter = 0
 	while not done:
 		done = True
@@ -110,8 +104,6 @@ def refine(g):
 	for node in g.V():
 		finalcolors.append(node.colornum)
 
-	elapsed_time = time.clock() - start_time
-	print('Time: {0:.4f} sec'.format(elapsed_time))
 	# DUS HIER SHIT DOEN MET COLORDICT EN DUBBELE KLEUREN ENZO
 	try:
 		result = compareColors(splitColorDict(colordict, g)[0])
@@ -141,8 +133,7 @@ def getNeighbourColors(v):
 		colors.append(i.colornum)
 	return colors
 
-
-def compare(graphlisturl=-1, gs=-1):
+def compare(graphlisturl=-1, GI_only=False, gs=-1):
 	assert graphlisturl != -1 or gs != -1
 
 	if gs is -1:
@@ -188,18 +179,16 @@ def compare(graphlisturl=-1, gs=-1):
 				if second > first:
 					print("First: ", first, ", Second: ", second)
 					tempgraph = disjointunion(graphlist[first], graphlist[second])
-					num = countIsomorphism(tempgraph, fastrefine(tempgraph))
+					num = countIsomorphism(tempgraph, fastrefine(tempgraph), GI_only)
 					if num > 0:
 						isomorphisms.append([first,second, num])
 
 	print('Search ended; Isomorphisms found: ', isomorphisms)
 
-	# individualization here
-
 	return colordict
 
 
-def countIsomorphism(graph, hasColordict=False):
+def countIsomorphism(graph, hasColordict=False, GI_only=False):
 	#print("CountIsomorphism bruh!")
 	if hasColordict is False:
[…]

### 2015-04-06 colorRefinement.py
-

@@ -394,6 +394,7 @@ def testpre(graphlisturl):
     print(graphlist[0][0])
     for i in range(ngraphs):
         writeDOT(graphlist[0][i], 'after' + str(i) + '.dot')
+    print(graphlist)
     return compare(gs=graphlist[0], preproc=True)
 
 

### 2015-04-06 GraphBasics/makegraphs.py
alles werkt?

@@ -1,44 +1,0 @@
-# DW 2 practicum, Ex1 solution
-from basicgraphs import graph
-
-
-def path(n):
-	P = graph(n)
-	for i in range(n - 1):
-		P.addedge(P[i], P[i + 1])
-	return P
-
-
-def cycle(n):
-	C = graph(n)
-	for i in range(n):
-		C.addedge(C[i], C[(i + 1) % n])
-	return C
-
-
-def complete(n):
-	K = graph(n)
-	for i in range(n - 1):
-		for j in range(i + 1, n):
-			K.addedge(K[i], K[j])
-	return K
-
-
-def disjointunion(G, H):
-	vmap = { }
-	K = graph()
-	for v in G.V() + H.V():
-		vmap[v] = K.addvertex()
-	for e in G.E() + H.E():
-		K.addedge(vmap[e.tail()], vmap[e.head()])
-	return K
-
-
-if __name__ == "__main__":
-	P = path(5)
-	C = cycle(5)
-	K = complete(4)
-	print(P)
-	print(C)
-	print(K)
-	print(disjointunion(disjointunion(P, C), K))

### 2015-04-06 colorRefinement.py

@@ -153,10 +153,17 @@ def compare(graphlisturl=-1, gs=-1, preproc=False):
     g = graphlist[0]
     subgraphlist = []
     subgraphlist.append(len(g.V()))
+    print(g)
     for i in range(1, len(graphlist)):  # make one big graph from the graphlist
+        print(i)
         h = graphlist[i]
         g = disjointunion(g, h)
+        print(h)
+        print(g)
         subgraphlist.append(len(h.V()))
+    print(g)
+    print('HIER')
+    print(subgraphlist)
     g.makenbsdict()  # update nbs omdat er een nieuwe graph is
     g.makeinclist()
     g.subgraphs = subgraphlist
@@ -391,10 +398,10 @@ def testpre(graphlisturl):
         # print(graphlist[0][i])
         #isgraph(graphlist[0][i])
     print('number of twins:', nfalsetwins, ntwins)
-    print(graphlist[0][0])
     for i in range(ngraphs):
+        print(graphlist[0][i])
         writeDOT(graphlist[0][i], 'after' + str(i) + '.dot')
-    print(graphlist)
+    print('graphs^')
     return compare(gs=graphlist[0], preproc=True)
 
 
@@ -412,10 +419,10 @@ def isgraph(g):
 # compare("GI_TestInstancesWeek1/crefBM_4_9.grl")
 # print(compare("GI_TestInstancesWeek1/threepaths10240.gr"))
 
-start_time = time.clock()
-print(compare("GI_TestInstancesWeek1/cographs1.grl"))
-elapsed_time = time.clock() - start_time
-print('total time: {0:.4f} sec'.format(elapsed_time))
+# start_time = time.clock()
+# print(compare("GI_TestInstancesWeek1/cographs1.grl"))
+# elapsed_time = time.clock() - start_time
+# print('total time: {0:.4f} sec'.format(elapsed_time))
 
 start_time = time.clock()
 print(testpre("GI_TestInstancesWeek1/cographs1.grl"))

### 2015-04-06 graphIO.py

@@ -23,232 +23,232 @@ numcolors = 12
 
 
 def readgraph(graphclass, readline):
-	"""
-	For internal use.
-	"""
-	options = []
-	while True:
-		try:
-			S = readline()
-			n = int(S)
-			G = graphclass(n)
-			break
-		except ValueError:
-			if len(S) > 0 and S[-1] == '\n':
-				options.append(S[:-1])
-			else:
-				options.append(S)
-	S = readline()
-	edgelist = []
-	try:
-		while True:
-			comma = S.find(',')
-			if ':' in S:
-				colon = S.find(':')
-				edgelist.append((int(S[:comma]), int(S[comma + 1:colon]), int(S[colon + 1:])))
-			else:
-				edgelist.append((int(S[:comma]), int(S[comma + 1:]), None))
-			S = readline()
-	except Exception:
-		pass
-	for edge in edgelist:
-		# print("Adding edge (%d,%d)"%(edge[0],edge[1]))
-		e = G.addedge(G[edge[0]], G[edge[1]])
-		if edge[2] != None:
-			e.weight = edge[2]
-	if S != '' and S[0] == '-':
-		return G, options, True
-	else:
-		return G, options, False
+    """
+    For internal use.
+    """
+    options = []
+    while True:
+        try:
+            S = readline()
+            n = int(S)
+            G = graphclass(n)
+            break
+        except ValueError:
+            if len(S) > 0 and S[-1] == '\n':
+                options.append(S[:-1])
+            else:
+                options.append(S)
+    S = readline()
+    edgelist = []
+    try:
+        while True:
+            comma = S.find(',')
+            if ':' in S:
+                colon = S.find(':')
+                edgelist.append((int(S[:comma]), int(S[comma + 1:colon]), int(S[colon + 1:])))
+            else:
+                edgelist.append((int(S[:comma]), int(S[comma + 1:]), None))
+            S = readline()
+    except Exception:
+        pass
+    for edge in edgelist:
+        # print("Adding edge (%d,%d)"%(edge[0],edge[1]))
+        e = G.addedge(G[edge[0]], G[edge[1]])
+        if edge[2] != None:
+            e.weight = edge[2]
+    if S != '' and S[0] == '-':
+        return G, options, True
+    else:
+        return G, options, False
 
 
 def readgraphlist(graphclass, readline):
-	"""
-	For internal use.
-	"""
-	options = []
-	L = []
-	contin = True
-	while contin:
[…]

### 2015-04-06 makegraphs.py

@@ -30,9 +30,9 @@ def disjointunion(G, H):
     vmap = {}
     K = graph()
     for v in G.V() + H.V():
-        vmap[v._label] = K.addvertex()
+        vmap[v] = K.addvertex()
     for e in G.E() + H.E():
-        K.addedge(vmap[e.tail()._label], vmap[e.head()._label])
+        K.addedge(vmap[e.tail()], vmap[e.head()])
     return K
 
 

### 2015-04-06 paper/paper.tex
verslag

@@
 
-Proof of Correctness here
+\begin{definition}
+Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs.
+A function $f: V_1 \to V_2$ is called a \textit{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$.
+When such a function exist, $G_1$ and $G_2$ are called \textit{ismorphic graphs}.
+\end{definition}
+\begin{definition}
+Let $G = (V,E)$ be a graph. The \textit{neighbourhood} $N(v)$ of $v \in V$ is:
+$N(v) = \left\{{u \in V : \{u,v\} \in E}\right\}$
+\end{definition}
+\begin{definition}
+Let $G = (V,E)$ be a graph.
+Two vertices $u, v \in V$ are \textit{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash {v} = N(v)\textbackslash {u}$.
+\end{definition}
+\begin{definition}
+Let $G = (V,E)$ be a graph.
+Two vertices $u, v \in V(G)$ are \textit{false twins} if $N(u) = N(v).$
+\end{definition}
 

### 2015-04-06 basicgraphs.py
Werkende versie

@@ -15,121 +15,125 @@ unsafe = False
 
 
 class GraphError(Exception):
-	def __init__(self, message):
-		self.mess = message
+    def __init__(self, message):
+        self.mess = message
 
-	def __str__(self):
-		return self.mess
+    def __str__(self):
+        return self.mess
 
 
 class vertex():
-	"""
+    """
     Vertex objects have an attribute <_graph> pointing to the graph they are part of,
     and an attribute <_label> which can be anything: it is not used for any methods,
     except for __repr__.
     """
-	colornum = None
+    colornum = None
 
-	nbl = -1
-	incl = -1
+    nbl = -1
+    incl = -1
 
-	def __init__(self, graph, label=0):
-		"""
+    def __init__(self, graph, label=0):
+        """
         Creates a vertex, part of <graph>, with optional label <label>.
         (Labels of different vertices may be chosen the same; this does
         not influence correctness of the methods, but will make the string
         representation of the graph ambiguous.)
         """
-		self._graph = graph
-		self._label = label
+        self._graph = graph
+        self._label = label
 
-	def __repr__(self):
-		return str(self._label)
+    def __repr__(self):
+        return str(self._label)
 
-	def adj(self, other):
-		"""
+    def adj(self, other):
+        """
         Returns True iff vertex <self> is adjacent to <other> vertex.
         """
-		return self._graph.adj(self, other)
+        return self._graph.adj(self, other)
 
-	def inclist(self):
-		"""
+    def inclist(self):
+        """
         Returns the list of edges incident with vertex <self>.
         """
-		if not self._graph.enlist:
-			self._graph.makeinclist()
-		return self._graph.enlist[self]
+        if not self._graph.enlist:
+            self._graph.makeinclist()
+        return self._graph.enlist[self]
 
-	def nbs(self):
-		"""
+    def nbs(self):
+        """
         Returns the list of neighbors of vertex <self>.
         In case of parallel edges: duplicates are not removed from this list!
         """
-		if self.nbl == -1:
-			self.nbl = []
-			for e in self.inclist():
-				self.nbl.append(e.otherend(self))
-		return self.nbl
+        if self.nbl == -1:
+            self.nbl = []
+            for e in self.inclist():
+                self.nbl.append(e.otherend(self))
+        return self.nbl
 
-	def deg(self):
-		"""
+    def fastnbs(self):
+        pass
+
+
+    def deg(self):
+        """
         Returns the degree of vertex <self>.
[…]

### 2015-04-06 colorRefinement.py

@@ -7,348 +7,427 @@ from makegraphs import disjointunion
 from graphIO import *
 
 
-def fastrefine(g, colordictarg=-1, startcolor=-1):
-	if colordictarg is -1:
-		if g.colordict == -1:
-			colordict = degcolordict(g)
-		else:
-			colordict = g.colordict
-	else:
-		colordict = colordictarg
-	if startcolor is -1:
-		shortest = min(colordict.keys())
-		for key in colordict.keys():
-			if len(colordict[key]) <= len(colordict[shortest]):
-				shortest = key
-		queue = [shortest]
-	else:
-		queue = [startcolor]
+def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
+    if colordictarg is -1:
+        if g.colordict == -1:
+            if not preproc:
+                colordict = degcolordict(g)
+            else:
+                colordict = preproccolordict(g)
+        else:
+            if not preproc:
+                colordict = g.colordict
+            else:
+                colordict = preproccolordict
+    else:
+        colordict = colordictarg
+    if startcolor is -1:
+        shortest = min(colordict.keys())
+        for key in colordict.keys():
+            if len(colordict[key]) <= len(colordict[shortest]):
+                shortest = key
+        queue = [shortest]
+    else:
+        queue = [startcolor]
 
-	applycolors(colordict)
-	nextcolor = max(colordict.keys()) + 1
+    applycolors(colordict)
+    nextcolor = max(colordict.keys()) + 1
 
-	i = 0
-	while i < len(queue):
-		connectednodes = dict()
-		for value in colordict[queue[i]]:
-			for nb in value.nbs():  # make colordict of neighbours
-				if nb.colornum not in connectednodes:
-					connectednodes[nb.colornum] = [nb]
-				elif nb not in connectednodes[nb.colornum]:
-					connectednodes[nb.colornum].append(nb)
+    i = 0
+    while i < len(queue):
+        connectednodes = dict()
+        for value in colordict[queue[i]]:
+            for nb in value.nbs():  # make colordict of neighbours
+                if nb.colornum not in connectednodes:
+                    connectednodes[nb.colornum] = [nb]
+                elif nb not in connectednodes[nb.colornum]:
+                    connectednodes[nb.colornum].append(nb)
 
-		for key in connectednodes.keys():
-			colordictchanged = False
-			colordict[key].sort(key=lambda x: x._label)
[…]

### 2015-04-06 basicgraphs.py
Werkende versie

@@ -71,10 +71,6 @@ class vertex():
                 self.nbl.append(e.otherend(self))
         return self.nbl
 
-    def fastnbs(self):
-        pass
-
-
     def deg(self):
         """
         Returns the degree of vertex <self>.
@@ -161,7 +157,6 @@ class graph():
         for i in range(n):
             self.addvertex()
         self.enlist = []
-        self.nbsdict = -1
         self.colordict = -1
         self.vertexreprmap = dict()
         for v in self._V:
@@ -202,21 +197,6 @@ class graph():
                 else:
                     r[e] = [edge]
         self.enlist = r
-
-    def makenbsdict(self):
-        nbsdict = {}  # key is a node, values are the adjacent nodes
-        for edge in self.E():
-            tail = edge.tail()
-            head = edge.head()
-            if tail in nbsdict.keys():
-                nbsdict[tail].append(head)
-            else:
-                nbsdict[tail] = [head]
-            if head in nbsdict.keys():
-                nbsdict[head].append(tail)
-            else:
-                nbsdict[head] = [tail]
-        self.nbsdict = nbsdict
 
     def V(self):
         """

### 2015-04-06 colorRefinement.py
Werkende versie

@@ -378,7 +378,7 @@ def preprocessing(g):
     return g, lftwins, ltwins
 
 
-def testpre(graphlisturl):
+def testpre(graphlisturl, GI_only=False):
     global graphlist
     graphlist = loadgraph(graphlisturl, readlist=True)
     ngraphs = len(graphlist[0])
@@ -392,7 +392,7 @@ def testpre(graphlisturl):
     print('number of twins:', nfalsetwins, ntwins)
     for i in range(ngraphs):
         writeDOT(graphlist[0][i], 'after' + str(i) + '.dot')
-    return compare(gs=graphlist[0], preproc=True)
+    return compare(gs=graphlist[0], preproc=True, GI_only=False)
 
 
 def findDuplicates(split2):

### 2015-04-06 colorRefinement.py
naamsverandering

@@ -378,20 +378,16 @@ def preprocessing(g):
     return g, lftwins, ltwins
 
 
-def testpre(graphlisturl, GI_only=False):
+def comparepreproc(graphlisturl, GI_only=False):
     global graphlist
     graphlist = loadgraph(graphlisturl, readlist=True)
     ngraphs = len(graphlist[0])
-    for i in range(ngraphs):
-        writeDOT(graphlist[0][i], 'before' + str(i) + '.dot')
     nfalsetwins, ntwins = [None] * ngraphs, [None] * ngraphs
     for i in range(ngraphs):
         graphlist[0][i], nfalsetwins[i], ntwins[i] = preprocessing(graphlist[0][i])
         # print(graphlist[0][i])
         # isgraph(graphlist[0][i])
     print('number of twins:', nfalsetwins, ntwins)
-    for i in range(ngraphs):
-        writeDOT(graphlist[0][i], 'after' + str(i) + '.dot')
     return compare(gs=graphlist[0], preproc=True, GI_only=False)
 
 
@@ -424,9 +420,9 @@ def findDuplicates(split2):
 
 start_time = time.clock()
 
-# compare("GI_TestInstancesWeek1/cographs1.grl", True)
+# compare("GI_TestInstancesWeek1/products72.grl", False)
 
-testpre("GI_TestInstancesWeek1/cographs1.grl")
+comparepreproc("GI_TestInstancesWeek1/products72.grl")
 
 elapsed_time = time.clock() - start_time
 print('a: {0:.4f} sec'.format(elapsed_time))

### 2015-04-06 colorRefinement.py
goede format

@@ -8,426 +8,434 @@ from graphIO import *
 
 
 def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
-    if colordictarg is -1:
-        if g.colordict == -1:
-            if not preproc:
-                colordict = degcolordict(g)
-            else:
-                colordict = preproccolordict(g)
-        else:
-            if not preproc:
-                colordict = g.colordict
-            else:
-                colordict = preproccolordict
-    else:
-        colordict = colordictarg
-    if startcolor is -1:
-        shortest = min(colordict.keys())
-        for key in colordict.keys():
-            if len(colordict[key]) <= len(colordict[shortest]):
-                shortest = key
-        queue = [shortest]
-    else:
-        queue = [startcolor]
+	if colordictarg is -1:
+		if g.colordict == -1:
+			if not preproc:
+				colordict = degcolordict(g)
+			else:
+				colordict = preproccolordict(g)
+		else:
+			if not preproc:
+				colordict = g.colordict
+			else:
+				colordict = preproccolordict
+	else:
+		colordict = colordictarg
+	if startcolor is -1:
+		shortest = min(colordict.keys())
+		for key in colordict.keys():
+			if len(colordict[key]) <= len(colordict[shortest]):
+				shortest = key
+		queue = [shortest]
+	else:
+		queue = [startcolor]
 
-    applycolors(colordict)
-    nextcolor = max(colordict.keys()) + 1
+	applycolors(colordict)
+	nextcolor = max(colordict.keys()) + 1
 
-    i = 0
-    while i < len(queue):
-        connectednodes = dict()
-        for value in colordict[queue[i]]:
-            for nb in value.nbs():  # make colordict of neighbours
-                if nb.colornum not in connectednodes:
-                    connectednodes[nb.colornum] = [nb]
-                elif nb not in connectednodes[nb.colornum]:
-                    connectednodes[nb.colornum].append(nb)
+	i = 0
+	while i < len(queue):
+		connectednodes = dict()
+		for value in colordict[queue[i]]:
+			for nb in value.nbs():  # make colordict of neighbours
+				if nb.colornum not in connectednodes:
+					connectednodes[nb.colornum] = [nb]
+				elif nb not in connectednodes[nb.colornum]:
+					connectednodes[nb.colornum].append(nb)
 
-        for key in connectednodes.keys():
-            colordictchanged = False
[…]

### 2015-04-06 colorRefinement.py
goede format

@@ -427,9 +427,9 @@ def findDuplicates(split2):
 
 start_time = time.clock()
 
-# compare("GI_TestInstancesWeek1/products72.grl", False)
+compare("GI_TestInstancesWeek1/cubes6.grl", True)
 
-comparepreproc("GI_TestInstancesWeek1/products72.grl")
+# comparepreproc("GI_TestInstancesWeek1/torus72.grl")
 
 elapsed_time = time.clock() - start_time
 print('Time: {0:.4f} sec'.format(elapsed_time))

### 2015-04-06 colorRefinement.py
ongebruikte code weg gepleurd

@@ -66,62 +66,6 @@ def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
 	return colordict
 
 
-def refine(g):
-	# initialize
-	colordict = degcolordict(g)
-
-	done = False
-	counter = 0
-	while not done:
-		done = True
-		counter += 1
-		if counter % 100 == 0:
-			print(counter)
-		tempcolordict = dict()
-
-		for key in colordict.keys():
-			nextcolor = max(colordict.keys()) + 1
-			buren = tuple()
-			for value in colordict[key]:
-				nc = sorted(tuple(getNeighbourColors(value)))
-				if len(buren) == 0:
-					buren = nc
-
-				if buren != nc:
-					done = False
-					if nextcolor in tempcolordict:
-						tempcolordict[nextcolor].append(value)
-					else:
-						tempcolordict[nextcolor] = [value]
-
-				else:
-					if key in tempcolordict:
-						tempcolordict[key].append(value)
-					else:
-						tempcolordict[key] = [value]
-
-		colordict = tempcolordict.copy()
-
-		for key in colordict.keys():
-			for value in colordict[key]:
-				value.colornum = key
-
-	finalcolors = []
-	for node in g.V():
-		finalcolors.append(node.colornum)
-
-	# DUS HIER SHIT DOEN MET COLORDICT EN DUBBELE KLEUREN ENZO
-	try:
-		result = compareColors(splitColorDict(colordict, g)[0])
-		if len(undecidedGraphs) > 0:
-			print(undecidedGraphs)
-			findDuplicates(splitColorDict(colordict, g)[1])
-		return result
-	except:
-		print('its only one graph apparently')
-		return colordict
-
-
 def degcolordict(g):
 	colordict = {}  # dictionary with key=c and value=vertex array
 	for v in g.V():
@@ -311,10 +255,6 @@ def compareColors(split):
 	return r, undecidedGraphs
 
 
-def splitlist(l, n):
-	return [l[i:i + n] for i in range(0, len(l), n)]
-
-
 def gettwins(g):
 	nbs = []
 	nbs2 = []
@@ -397,33 +337,6 @@ def comparepreproc(graphlisturl, GI_only=False):
     print('number of twins:', nfalsetwins, ntwins)
     return compare(gs=graphlist[0], preproc=True, GI_only=False)
 
-
-def findDuplicates(split2):
[…]

### 2015-04-06 IndividualizationRefinement.py
ongebruikte file foetsie

@@ -1,5 +1,0 @@
-__author__ = 'Jeroen'
-
-
-def ind_refinement():
-	return 0

### 2015-04-06 colorRefinement.py

@@ -340,7 +340,7 @@ def comparepreproc(graphlisturl, GI_only=False):
 
 start_time = time.clock()
 
-compare("GI_TestInstancesWeek1/cubes6.grl", True)
+compare("GI_TestInstancesWeek1/bigtrees3.grl", True)
 
 # comparepreproc("GI_TestInstancesWeek1/torus72.grl")
 

### 2015-04-06 colorRefinement.py
alles werkt!! :DDDDD

@@ -21,6 +21,7 @@ def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
 				colordict = preproccolordict
 	else:
 		colordict = colordictarg
+
 	if startcolor is -1:
 		shortest = min(colordict.keys())
 		for key in colordict.keys():
@@ -65,6 +66,54 @@ def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
 		i += 1
 	return colordict
 
+
+def fastrefine2(g, colordictarg=-1, startcolor=-1, preproc=False):
+	# initialize
+	if colordictarg == -1:
+		colordict = degcolordict(g)
+	else:
+		colordict = colordictarg
+
+	done = False
+	counter = 0
+	while not done:
+		done = True
+		counter += 1
+		if counter % 100 == 0:
+			print(counter)
+		tempcolordict = dict()
+
+		for key in colordict.keys():
+			nextcolor = max(colordict.keys()) + 1
+			buren = tuple()
+			for value in colordict[key]:
+				nc = sorted(tuple(getNeighbourColors(value)))
+				if len(buren) == 0:
+					buren = nc
+
+				if buren != nc:
+					done = False
+					if nextcolor in tempcolordict:
+						tempcolordict[nextcolor].append(value)
+					else:
+						tempcolordict[nextcolor] = [value]
+
+				else:
+					if key in tempcolordict:
+						tempcolordict[key].append(value)
+					else:
+						tempcolordict[key] = [value]
+
+		colordict = tempcolordict.copy()
+
+		for key in colordict.keys():
+			for value in colordict[key]:
+				value.colornum = key
+
+	finalcolors = []
+	for node in g.V():
+		finalcolors.append(node.colornum)
+	return colordict
 
 def degcolordict(g):
 	colordict = {}  # dictionary with key=c and value=vertex array
@@ -116,19 +165,27 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 		colordict = fastrefine(g, preproc=True)
 	else:
 		colordict = fastrefine(g)
-	graphcolors = splitColorDict(colordict, g)[0]
-
+	graphcolors = splitColorDict(colordict, g)[0]  # is a list of colordicts
+	print(graphcolors)
 	isomorphisms = []
 	undecided = []
-	for i in range(len(graphcolors)):  # find isomorphisms
-		if len(list(set(graphcolors[i]))) != len(graphcolors[i]):
-			undecided.append(i)
-		else:
[…]

### 2015-04-07 paper/paper.tex
copies paper from devnew

@@
 \usepackage[utf8]{inputenc} % UTF-8 character encoding stuff
+\usepackage[toc,page]{appendix} % appendix
 
-% Used to enable use of the defined labeled enunciations. Usage: \begin{definition}text\end{definition}
-\newtheorem{theorem}{Theorem}[section]
+% Used to enable use of the defined labeled enunciations. Usage: 
+%\begin{definition}text\end{definition}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}
 \newtheorem{lemma}[theorem]{Lemma}
@@
 \newtheorem{corollary}[theorem]{Corollary}
+
+% Python code
+
+\usepackage{listings}
+\lstset{
+numbers=left
+}
 
@@
 
-The preprocessing part are algorithms that look at the graphs before determining whether they are isomorphic with the intent of speeding up the actual process of the determining whether the graphs are isomorphic.
+The preprocessing part are algorithms that look at the graphs before determining whether they are isomorphic with the intent of finding some characteristic that might be used to speed up the actual process of the determining whether the graphs are isomorphic.
 
@@
 For this paper, the time complexity of the algorithms will not be discussed or calculated.
-The difference in performance of the cases will be shown from a statistical analysis of computational results.
+The difference in performance between the cases will be shown with a statistical analysis on computational results.
 
-This paper will give a description of the algorithms used for preproccesing, as well as proof of correctness. The algorithms used to check for isomorphisms will be left out of consideration.
+This paper will give a description of the algorithms used for preprocessing, as well as proof of correctness. The algorithms used to check for isomorphisms will be left out of consideration.
 
@@
 \section{Methods}
+To determine whether the algorithms will speed up the process of finding graph isomorphisms, a computational experiment was performed.
+In this experiment, the algorithms were used on a variety of differently shaped graphs, and sets of graphs, in conjunction with an algorithm which checks for isomorphisms.
 
-TBD - exact setup of experiment - what methods were used to test
-Used to examine validity of the experiment by outsiders, by very precise, give reasons for methods and setup, possibly give alternatives and arguments for them, but describe why we chose the current methods.
+\subsection{Experiment Setup}
+For the testing, a single laptop was used to collect all the timed data.
+The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code.
+The python interpreter used was Python 3.4 and the laptop was running Windows 8.1 at the time of the testing.
+Efforts were made to ensure all the testing was performed under the same circumstances.
+
+\subsection{Testing}
+In the experiment, two cases were tested: a basic case, without preprocessing, and a case with preprocessing.
+In both cases a timer was added to the code.
+The timer started before any other piece of code, and ended only after the algorithms were completely finished.
+This way everything is timed, including the loading of the graph, the additional time used to run preprocessing algorithms and finding of the isomorphisms.
+
+For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared and tested...
+\\ \\
+\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct; what statistical tests are we using?}
 
@@
 \section{Description of Algorithms}
-
-Description of Algorithms here
-Don't forget to reference the slides
-
-%------------------------------------------------
-\section{Proof of Correctness}
-
-\begin{definition}
-Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs.
-A function $f: V_1 \to V_2$ is called a \textit{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$.
-When such a function exist, $G_1$ and $G_2$ are called \textit{ismorphic graphs}.
-\end{definition}
+For hard instances of the graph isomorphism problem, the coarsest stable coloring of a graph still has a lot of colors which are not unique.
+Two structures for which this is the case are twins and false twins, they are defined in definition \ref{deftwins} and \ref{deffalsetwins}.
 \begin{definition}
@@
 \end{definition}
-\begin{definition}
+\begin{definition}\label{deftwins}
 Let $G = (V,E)$ be a graph.
@@
 \end{definition}
-\begin{definition}
+\begin{definition}\label{deffalsetwins}
 Let $G = (V,E)$ be a graph.
@@
 
+To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
+\begin{enumerate}
+\item Twins have the same color $\iff$ Twins have the same size (number of vertices).
+\item False twins have the same color $\iff$ False twins have the same size (number of vertices).
+\item A twin and a false twin can't have the same color.
+\end{enumerate}
+\subsection{Implementation}
+The algorithm is divided into two subalgorithms.
+The subalgorithm \textit{gettwins} finds all twins and false twins and the subalgorithm \textit{preprocessing} replaces each (false) twin by a single colored vertex as described above.
+In the following subsections these algorithms and their worst case time complexities will be analyzed.
+The elementary operation is the comparison of two elements.
+In those subsections $n$ is the number of vertices of a graph $G(V,E)$ and $m$ is the number of edges of that graph.
+
+\subsubsection{Finding twins and false twins}
+The algorithm \textit{gettwins} can be found in appendix \ref{gettwins}.
+In line 2-10 two lists, \textit{nbs} and \textit{nbs2}, are created.
+Both lists contains $n$ sorted sublists.
+In the former list each sublist contains all the neighbours of a node and in the latter each sublist contains all the neighbours of a node and also the node itself.
+Finding all the neighbours only require going though all the edges once, so the time complexity is $O(m)$.
+The sorting algorithm has time complexity $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$.
+\\\newline In line 11-16 a dictionary \textit{falsetwins} is created where the keys are all the items from \textit{nbs} and the values a list of the corresponding vertices.
+Since \textit{nbs} has length $n$ and \textit{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$.
+In line 23 the items in the \textit{falsetwins} with only one vertex as value are removed.
+This is $O(n)$, since len() has $O(1)$.
+The remaining values of the dictionary \textit{falsetwins} are now all the sets of false twins as defined in definition \ref{deffalsetwins}.
+A similar dictionary \textit{twins} is created where the keys are the items from \textit{nbs2}.
+The time complexity of \textit{gettwins} is thus $O(n^2 \log n)$.
+%BRON https://wiki.python.org/moin/TimeComplexity
+
+\subsubsection{Replacing the twins}
+Similar to 4.1
+
+%------------------------------------------------
+\section{Proof of Correctness}
+NOG NIET AF!
+\begin{definition}
+A \textit{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
+\end{definition}
+\begin{definition}
+Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs.
+A function $f: V_1 \to V_2$ is called a \textit{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$.
+When such a function exist, $G_1$ and $G_2$ are called \textit{isomorphic graphs}.
+\end{definition}
+\begin{theorem}
+Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs where each vertex has the same color and let $H_1 = (V_1, E_1)$ and $H_2 = (V_2, E_2)$ be resp.
+the same graphs as $G_1$ and $G_2$ where each twin is replaced by a colored vertex such that (a) Each twin
+\end{theorem}
+
+%bron http://pages.cs.wisc.edu/~dieter/Papers/3gi.pdf
+
 %------------------------------------------------
@@
 
-Computational Experiments here
+Computational Experiments here\\
 Setup good experiments beforehand and test extensively
@@
 
-Results here
+Results here \\
 And statistical analysis of the results
@@
 
-Conclusions here 
+Conclusions here \\
 Is it faster?
@@
 \end{multicols}
+\begin{appendices}
+
+\section{Python code}
+\lstset{language=Python}
+\begin{lstlisting}[label={gettwins}]
+def gettwins(g):
+    nbs = []
+    nbs2 = []
+    for vertex in g.V():
+        nb = vertex.nbs()[:]
+        nb.sort(key=lambda x: x._label)
+        nbs.append(tuple(nb))
+        nb.append(vertex)
+        nb.sort(key=lambda x: x._label)
+        nbs2.append(tuple(nb))
+    falsetwins = {}
+    for i, item in enumerate(nbs):
+        if item in falsetwins.keys():
+            falsetwins[item].append(g.V()[i])
+        else:
+            falsetwins[item] = [g.V()[i]]
+    twins = {}
+    for i, item in enumerate(nbs2):
+        if item in twins.keys():
+            twins[item].append(g.V()[i])
+        else:
+            twins[item] = [g.V()[i]]
+    falsetwins = {k: v for k, v in falsetwins.items() if len(v) > 1}
+    twins = {k: v for k, v in twins.items() if len(v) > 1}
+    return list(falsetwins.values()), list(twins.values()), list(falsetwins.keys()), list(twins.keys())   
+\end{lstlisting}
+\end{appendices}
 
 \end{document}
+Status API Training Shop Blog About
+© 2015 GitHub, Inc. Terms Privacy Security Contact

### 2015-04-07 paper/paper.tex
copies paper from devnew
verslag

@@
 Finding all the neighbours only require going though all the edges once, so the time complexity is $O(m)$.
-The sorting algorithm has time complexity $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$.
+The sorting algorithm has time complexity $O(n \log n)$, since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$.
+In most test instances the average length of the neighbours is however not even close to $n$, so this really is a worst case complexity.
 \\\newline In line 11-16 a dictionary \textit{falsetwins} is created where the keys are all the items from \textit{nbs} and the values a list of the corresponding vertices.

### 2015-04-07 paper/paper.tex
paper updates

--- 2015-04-07 paper/paper.tex
@@
 % Python code
-
 \usepackage{listings}
 \lstset{
-numbers=left
+numbers=left,
+breaklines=true
 }
@@
 % Bibliography
-\usepackage[backend=bibtex]{biblatex}
+\usepackage[backend=bibtex, sorting=none]{biblatex}
 \bibliography{references.bib}
@@
 
-For this paper, the time complexity of the algorithms will not be discussed or calculated.
-The difference in performance between the cases will be shown with a statistical analysis on computational results.
+For this paper, the time complexity of the algorithms will be calculated.
+The difference in performance between the cases will be shown with a statistical analysis on computational results as well as the calculated time complexities.
 
@@
 \begin{definition}
-Let $G = (V,E)$ be a graph. The \textit{neighbourhood} $N(v)$ of $v \in V$ is:
+Let $G = (V,E)$ be a graph. The \emph{neighbourhood} $N(v)$ of $v \in V$ is:
 $N(v) = \left\{{u \in V : \{u,v\} \in E}\right\}$
@@
 Let $G = (V,E)$ be a graph.
-Two vertices $u, v \in V$ are \textit{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash {v} = N(v)\textbackslash {u}$.
+Two vertices $u, v \in V$ are \emph{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash {v} = N(v)\textbackslash {u}$.
 \end{definition}
@@
 Let $G = (V,E)$ be a graph.
-Two vertices $u, v \in V(G)$ are \textit{false twins} if $N(u) = N(v).$
+Two vertices $u, v \in V(G)$ are \emph{false twins} if $N(u) = N(v).$
 \end{definition}
@@
 To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
-\begin{enumerate}
+\begin{compactenum}
 \item Twins have the same color $\iff$ Twins have the same size (number of vertices).
@@
 \item A twin and a false twin can't have the same color.
-\end{enumerate}
+\end{compactenum}
 \subsection{Implementation}
@@
 \subsubsection{Finding twins and false twins}
-The algorithm \textit{gettwins} can be found in appendix \ref{gettwins}.
-In line 2-10 two lists, \textit{nbs} and \textit{nbs2}, are created.
+The algorithm \emph{gettwins} can be found in appendix \ref{gettwins}.
+In line 2-10 two lists, \emph{nbs} and \emph{nbs2}, are created.
 Both lists contains $n$ sorted sublists.
@@
 The sorting algorithm has time complexity $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$.
-\\\newline In line 11-16 a dictionary \textit{falsetwins} is created where the keys are all the items from \textit{nbs} and the values a list of the corresponding vertices.
-Since \textit{nbs} has length $n$ and \textit{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$.
-In line 23 the items in the \textit{falsetwins} with only one vertex as value are removed.
-This is $O(n)$, since len() has $O(1)$.
-The remaining values of the dictionary \textit{falsetwins} are now all the sets of false twins as defined in definition \ref{deffalsetwins}.
-A similar dictionary \textit{twins} is created where the keys are the items from \textit{nbs2}.
+
+In line 11-16 a dictionary \emph{falsetwins} is created where the keys are all the items from \emph{nbs} and the values a list of the corresponding vertices.
+Since \emph{nbs} has length $n$ and \emph{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$.
+In line 23 the items in the \emph{falsetwins} with only one vertex as value are removed.
+This is $O(n)$, since len() has $O(1)$.\cite{website:pythonTimeComplexity} The remaining values of the dictionary \emph{falsetwins} are now all the sets of false twins as defined in definition \ref{deffalsetwins}.
+A similar dictionary \emph{twins} is created where the keys are the items from \emph{nbs2}.
 The time complexity of \textit{gettwins} is thus $O(n^2 \log n)$.
-%BRON https://wiki.python.org/moin/TimeComplexity
 
@@
 \begin{definition}
-A \textit{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
+A \emph{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
 \end{definition}
@@
 Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs.
-A function $f: V_1 \to V_2$ is called a \textit{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$.
-When such a function exist, $G_1$ and $G_2$ are called \textit{isomorphic graphs}.
+A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$.
+When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}.
 \end{definition}

### 2015-04-07 paper/paper.tex
paper updates

@@
 For this paper, the time complexity of the algorithms will be calculated.
-The difference in performance between the cases will be shown with a statistical analysis on computational results as well as the calculated time complexities.
+The difference in performance between the cases will be shown by computational results as well as the calculated time complexities.
 
@@
 
-For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared and tested...
+For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared.
 \\ \\
-\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct; what statistical tests are we using?}
+\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct}
 
@@
 \end{compactenum}
+
 \subsection{Implementation}
@@
 
-Results here \\
-And statistical analysis of the results
+Results here
 
@@
 \end{document}
-Status API Training Shop Blog About
-© 2015 GitHub, Inc. Terms Privacy Security Contact

### 2015-04-07 paper/paper.tex
paper updates
verslag

@@
 For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared.
-\\ \\
-\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct}
 
@@
 \subsubsection{Replacing the twins}
-Similar to 4.1
+The algorithm \emph{preprocessing} can be found in appendix \ref{preprocessing}.
+In line 2 the twins and falsetwins are defined and if there are none the program will terminate.
+If there are any twins all edges with a head or tail in one of these twins will be deleted.
+The complexity of this is $O(m +$ number of vertices (\emph{twins}+\emph{falsetwins}))$ < O (nm)$.
+Then in line 13-19 all vertices which are in twins or falsetwins will be removed.
+The complexity of this is $O(n^2)$.
+In line 20-28 a new colored vertex will be added for each (false) twin $(O(n)$ and finnaly the edges from these vertices will be added ($O(n^2 (n+m)$).
+The worst case complexity of this algorithm is ($O(n^2 (n+m)$), however in average there are much less (false) twins than vertices (there are at most $n/2$).
+These twins also have much less than $n$ neighbours.
 
@@
 \end{multicols}
+\newpage
 \begin{appendices}
@@
 \end{lstlisting}
+
+\begin{lstlisting}[label={preprocessing}]
+def preprocessing(g):
+	falsetwins, twins, falsetwinsN, twinsN = gettwins(g)
+	lftwins = len(falsetwins)
+	ltwins = len(twins)
+	if lftwins != 0 or ltwins != 0:
+		deledges = []
+		for i, e in enumerate(g._E):
+			if any(e._tail in ftwin for ftwin in falsetwins) or any(e._head in ftwin for ftwin in falsetwins) or any(e._tail in twin for twin in twins) or any(e._head in twin for twin in twins):
+				deledges.append(i)
+		deledges.sort(reverse=True)
+		for i in deledges:
+			g._E.pop(i)
+		delnodes = []
+		for i, V in enumerate(g._V):
+			if any(V in ftwin for ftwin in falsetwins) or any(V in twin for twin in twins):
+				delnodes.append(i)
+		delnodes.sort(reverse=True)
+		for i in delnodes:
+			g._V.pop(i)
+		combined = falsetwinsN + twinsN
+		mx = 0
+		for i, twin in enumerate(falsetwins):
+			g.addvertexobject(twin[0], True, len(twin))
+			twin[0].colornum = -twin[0].twinsize
+			mx = max(mx, len(twin))
+		for i, twin in enumerate(twins):
+			g.addvertexobject(twin[0], True, len(twin) + mx)
+			twin[0].colornum = -twin[0].twinsize - mx
+		for i, twin in enumerate(falsetwins + twins):
+			for j in combined[i]:
+				if j in g.V() and twin[0] != j and not g.findedge(twin[0],k)
+					g.addedge(twin[0], j)
+		g._V.sort(key=lambda x: x._label)
+	return g, lftwins, ltwins
+\end{lstlisting}
+
 \end{appendices}

### 2015-04-07 paper/paper.tex
paper updates

@@
 numbers=left,
-breaklines=true
+breaklines=true,
+tabsize=4
 }
@@
 Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs where each vertex has the same color and let $H_1 = (V_1, E_1)$ and $H_2 = (V_2, E_2)$ be resp.
-the same graphs as $G_1$ and $G_2$ where each twin is replaced by a colored vertex such that (a) Each twin
-\end{theorem}
+the same graphs as $G_1$ and $G_2$ where each (false) twin is replaced by a colored vertex such that: \begin{enumerate}
+\item Twins (False twins) have the same color $\iff$ Twins (False twins) have the same size (number of vertices).
+\item A twin and a false twin can't have the same color.
+\end{enumerate}
+Graph $G_1$ and $G_2$ are isomorphic $\iff$ Graph $H_1$ and $H_2$ are isomorphic.
+\begin{proof}
+Todo
+\end{proof}
 

### 2015-04-07 paper/paper.tex
Start of results

--- 2015-04-07 paper/paper.tex
@@
 % Python code
+
 \usepackage{listings}
 \lstset{
-numbers=left,
-breaklines=true
+numbers=left
 }
@@
 % Bibliography
-\usepackage[backend=bibtex, sorting=none]{biblatex}
+\usepackage[backend=bibtex]{biblatex}
 \bibliography{references.bib}
@@
 
-For this paper, the time complexity of the algorithms will be calculated.
-The difference in performance between the cases will be shown by computational results as well as the calculated time complexities.
+For this paper, the time complexity of the algorithms will not be discussed or calculated.
+The difference in performance between the cases will be shown with a statistical analysis on computational results.
 
@@
 The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code.
-The python interpreter used was Python 3.4 and the laptop was running Windows 8.1 at the time of the testing.
+The python interpreter used was Python 3.4 and the laptop was running Windows 8.1 @ 1.6 GHz/ 3.67GB RAM at the time of the testing.
 Efforts were made to ensure all the testing was performed under the same circumstances.
@@
 
-For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared.
+For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared and tested...
 \\ \\
-\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct}
+\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct; what statistical tests are we using?}
 
@@
 \begin{definition}
-Let $G = (V,E)$ be a graph. The \emph{neighbourhood} $N(v)$ of $v \in V$ is:
+Let $G = (V,E)$ be a graph. The \textit{neighbourhood} $N(v)$ of $v \in V$ is:
 $N(v) = \left\{{u \in V : \{u,v\} \in E}\right\}$
@@
 Let $G = (V,E)$ be a graph.
-Two vertices $u, v \in V$ are \emph{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash {v} = N(v)\textbackslash {u}$.
+Two vertices $u, v \in V$ are \textit{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash {v} = N(v)\textbackslash {u}$.
 \end{definition}
@@
 Let $G = (V,E)$ be a graph.
-Two vertices $u, v \in V(G)$ are \emph{false twins} if $N(u) = N(v).$
+Two vertices $u, v \in V(G)$ are \textit{false twins} if $N(u) = N(v).$
 \end{definition}
@@
 To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
-\begin{compactenum}
+\begin{enumerate}
 \item Twins have the same color $\iff$ Twins have the same size (number of vertices).
@@
 \item A twin and a false twin can't have the same color.
-\end{compactenum}
-
+\end{enumerate}
 \subsection{Implementation}
@@
 \subsubsection{Finding twins and false twins}
-The algorithm \emph{gettwins} can be found in appendix \ref{gettwins}.
-In line 2-10 two lists, \emph{nbs} and \emph{nbs2}, are created.
+The algorithm \textit{gettwins} can be found in appendix \ref{gettwins}.
+In line 2-10 two lists, \textit{nbs} and \textit{nbs2}, are created.
 Both lists contains $n$ sorted sublists.
@@
 The sorting algorithm has time complexity $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$.
-
-In line 11-16 a dictionary \emph{falsetwins} is created where the keys are all the items from \emph{nbs} and the values a list of the corresponding vertices.
-Since \emph{nbs} has length $n$ and \emph{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$.
-In line 23 the items in the \emph{falsetwins} with only one vertex as value are removed.
-This is $O(n)$, since len() has $O(1)$.\cite{website:pythonTimeComplexity} The remaining values of the dictionary \emph{falsetwins} are now all the sets of false twins as defined in definition \ref{deffalsetwins}.
-A similar dictionary \emph{twins} is created where the keys are the items from \emph{nbs2}.
+\\\newline In line 11-16 a dictionary \textit{falsetwins} is created where the keys are all the items from \textit{nbs} and the values a list of the corresponding vertices.
+Since \textit{nbs} has length $n$ and \textit{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$.
+In line 23 the items in the \textit{falsetwins} with only one vertex as value are removed.
+This is $O(n)$, since len() has $O(1)$.
+The remaining values of the dictionary \textit{falsetwins} are now all the sets of false twins as defined in definition \ref{deffalsetwins}.
+A similar dictionary \textit{twins} is created where the keys are the items from \textit{nbs2}.
 The time complexity of \textit{gettwins} is thus $O(n^2 \log n)$.
+%BRON https://wiki.python.org/moin/TimeComplexity
 
@@
 \begin{definition}
-A \emph{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
+A \textit{colored} graph $G(E,V)$ is a graph where each vertex $v \in V$ has a color label.
 \end{definition}
@@
 Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs.
-A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$.
-When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}.
+A function $f: V_1 \to V_2$ is called a \textit{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$.
+When such a function exist, $G_1$ and $G_2$ are called \textit{isomorphic graphs}.
 \end{definition}
@@
 %------------------------------------------------
-\section{Computational Experiments}
-
-Computational Experiments here\\
-Setup good experiments beforehand and test extensively
-
-%------------------------------------------------
 \section{Results}
 
-Results here
+Results here \\
+And statistical analysis of the results
 
@@
 \end{lstlisting}
+
+\section{Table with computation times}
+\begin{tabular}{c|c|c}
+Graph & Computation time (without preprocessing) & Computation time (with preprocessing) \\
+\hline
+cographs1 & 146.8098 sec & 0.0171 sec \\
+hugecographs & >30 min & 662.5381 sec \\
+cycles175 & 69.8579 & 70.8041 sec \\
+bigtrees3 & -1 & -1\\
+cubes6 & -1 & -1\\
+products72 & -1 & -1\\
+torus72 & -1 & -1\\
+
+\end{tabular}
 \end{appendices}
@@
 \end{document}
+Status API Training Shop Blog About
+© 2015 GitHub, Inc. Terms Privacy Security Contact

### 2015-04-07 paper/paper.tex

--- 2015-04-07 paper/paper.tex
@@
 numbers=left,
-breaklines=true,
-tabsize=4
+breaklines=true
 }
@@
 
+\section{Table with computation times}
+\begin{tabular}{c|c|c}
+Graph & Computation time (without preprocessing) & Computation time (with preprocessing) \\
+\hline
+cographs1 & 146.8098 sec & 0.0171 sec \\
+hugecographs & >30 min & 662.5381 sec \\
+cycles175 & 69.8579 & 70.8041 sec \\
+bigtrees3 & -1 & -1\\
+cubes6 & -1 & -1\\
+products72 & -1 & -1\\
+torus72 & -1 & -1\\
+
+\end{tabular}
+
 \begin{lstlisting}[label={preprocessing}]

### 2015-04-07 colorRefinement.py
naamsverandering

@@ -393,23 +393,23 @@ def preprocessing(g):
 
 
 def comparepreproc(graphlisturl, GI_only=False):
-    global graphlist
-    graphlist = loadgraph(graphlisturl, readlist=True)
-    ngraphs = len(graphlist[0])
-    nfalsetwins, ntwins = [None] * ngraphs, [None] * ngraphs
-    for i in range(ngraphs):
-        graphlist[0][i], nfalsetwins[i], ntwins[i] = preprocessing(graphlist[0][i])
-        # print(graphlist[0][i])
-        # isgraph(graphlist[0][i])
-    print('number of twins:', nfalsetwins, ntwins)
-    return compare(gs=graphlist[0], preproc=True, GI_only=False)
+	global graphlist
+	graphlist = loadgraph(graphlisturl, readlist=True)
+	ngraphs = len(graphlist[0])
+	nfalsetwins, ntwins = [None] * ngraphs, [None] * ngraphs
+	for i in range(ngraphs):
+		graphlist[0][i], nfalsetwins[i], ntwins[i] = preprocessing(graphlist[0][i])
+	# print(graphlist[0][i])
+	# isgraph(graphlist[0][i])
+	print('number of twins:', nfalsetwins, ntwins)
+	return compare(gs=graphlist[0], preproc=True, GI_only=False)
 
 
 start_time = time.clock()
 
-compare("GI_TestInstancesWeek1/cubes6.grl", True)
+# compare("GI_TestInstancesWeek1/products72.grl", False)
 
-# comparepreproc("GI_TestInstancesWeek1/torus72.grl")
+comparepreproc("GI_TestInstancesWeek1/cographs1.grl")
 
 elapsed_time = time.clock() - start_time
 print('Time: {0:.4f} sec'.format(elapsed_time))

### 2015-04-07 paper/paper.tex
naamsverandering
paper updates

--- 2015-04-07 paper/paper.tex
@@
 \begin{definition}
-Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs.
-A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if (a) $f$ is a bijection, (b) for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and (c) $color(v)$ = $color (f(v)$.
-When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}.
+Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if \begin{compactenum}[\upshape(a)]
+\item $f$ is a bijection, 
+\item for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and 
+\item $color(v)$ = $color (f(v)$. When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}. 
+\end{compactenum}
 \end{definition}
@@
 Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs where each vertex has the same color and let $H_1 = (V_1, E_1)$ and $H_2 = (V_2, E_2)$ be resp.
-the same graphs as $G_1$ and $G_2$ where each (false) twin is replaced by a colored vertex such that: \begin{enumerate}
+the same graphs as $G_1$ and $G_2$ where each (false) twin is replaced by a colored vertex such that: \begin{compactenum}[\upshape(a)]
 \item Twins (False twins) have the same color $\iff$ Twins (False twins) have the same size (number of vertices).
 \item A twin and a false twin can't have the same color.
-\end{enumerate}
+\end{compactenum}
 Graph $G_1$ and $G_2$ are isomorphic $\iff$ Graph $H_1$ and $H_2$ are isomorphic.
+\end{theorem}
 \begin{proof}

### 2015-04-07 paper/paper.tex

@@
 
+\section{Table with computation times}
+\begin{tabular}{c|c|c}
+Graph & Computation time (without preprocessing) & Computation time (with preprocessing) \\
+\hline
+cographs1 & 146.8098 sec & 0.0171 sec \\
+hugecographs & >30 min & 662.5381 sec \\
+cycles175 & 69.8579 & 70.8041 sec \\
+bigtrees3 & -1 & -1\\
+cubes6 & -1 & -1\\
+products72 & -1 & -1\\
+torus72 & -1 & -1\\
+
 \end{appendices}

### 2015-04-07 colorRefinement.py
readme gemaakt

@@ -199,8 +199,6 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 	for tuple in undecided:
 		first = tuple[0]
 		second = tuple[1]
-
-		print("Doing ", [first, second])
 		tempgraph = disjointunion(graphlist[first], graphlist[second])
 		num = countIsomorphism(tempgraph, fastrefine(tempgraph), GI_only)
 		if num > 0:
@@ -239,7 +237,7 @@ def countIsomorphism(graph, hasColordict=False, GI_only=False):
 			return 0
 		# if length == 2:
 		# if int(colordict[c][0].__repr__()) <= int(graph.subgraphs[0]) < int(colordict[c][1].__repr__()):
-		# 		pass
+		# pass
 		# 	else:
 		# 		return 0
 	if isomorphism:
@@ -273,8 +271,6 @@ def countIsomorphism(graph, hasColordict=False, GI_only=False):
 			num += countIsomorphism(graph2, colordict2, GI_only)
 	return num
 
-	return 0
-
 
 def applycolors(colordict):
 	for color in colordict.keys():
@@ -304,7 +300,7 @@ def splitColorDict(colordict, g):
 						split[partitions.index(e)][key] = [value]
 					# split[partitions.index(e)].append(value.colornum)
 					split2[partitions.index(e)].append((value.colornum, value))
-	#print('split', split)
+	# print('split', split)
 	return split, split2
 
 
@@ -408,13 +404,15 @@ def comparepreproc(graphlisturl, GI_only=False):
 	return compare(gs=graphlist[0], preproc=True, GI_only=True)
 
 
-
-
 start_time = time.clock()
 
-# compare("GI_TestInstancesWeek1/products72.grl", False)
+compare("GI_TestInstancesWeek1/products72.grl", False)  # #aut for product72
+compare("GI_TestInstancesWeek1/torus72.grl", False)  # #aut for torus72
+compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
+compare("GI_TestInstancesWeek1/bigtrees3.grl", True)  # GI for bigtrees3
 
-comparepreproc("GI_TestInstancesWeek1/cubes6.grl")
+comparepreproc("GI_TestInstancesWeek1/cographs1.grl")  # GI for cographs1 with preprocessing
[…]

### 2015-04-07 basicgraphs.py
component

@@ -15,286 +15,288 @@ unsafe = False
 
 
 class GraphError(Exception):
-    def __init__(self, message):
-        self.mess = message
+	def __init__(self, message):
+		self.mess = message
 
-    def __str__(self):
-        return self.mess
+	def __str__(self):
+		return self.mess
 
 
 class vertex():
-    """
-    Vertex objects have an attribute <_graph> pointing to the graph they are part of,
-    and an attribute <_label> which can be anything: it is not used for any methods,
-    except for __repr__.
-    """
-    colornum = None
+	"""
+	Vertex objects have an attribute <_graph> pointing to the graph they are part of,
+	and an attribute <_label> which can be anything: it is not used for any methods,
+	except for __repr__.
+	"""
+	colornum = None
 
-    nbl = -1
-    incl = -1
+	nbl = -1
+	incl = -1
+	visited = False
+	component = 0
 
-    def __init__(self, graph, label=0):
-        """
-        Creates a vertex, part of <graph>, with optional label <label>.
-        (Labels of different vertices may be chosen the same; this does
-        not influence correctness of the methods, but will make the string
-        representation of the graph ambiguous.)
-        """
-        self._graph = graph
-        self._label = label
+	def __init__(self, graph, label=0):
+		"""
+		Creates a vertex, part of <graph>, with optional label <label>.
+		(Labels of different vertices may be chosen the same; this does
+		not influence correctness of the methods, but will make the string
+		representation of the graph ambiguous.)
+		"""
+		self._graph = graph
+		self._label = label
 
-    def __repr__(self):
-        return str(self._label)
+	def __repr__(self):
+		return str(self._label)
 
-    def adj(self, other):
-        """
-        Returns True iff vertex <self> is adjacent to <other> vertex.
-        """
-        return self._graph.adj(self, other)
+	def adj(self, other):
+		"""
+		Returns True iff vertex <self> is adjacent to <other> vertex.
+		"""
+		return self._graph.adj(self, other)
 
-    def inclist(self):
-        """
-        Returns the list of edges incident with vertex <self>.
-        """
-        if not self._graph.enlist:
-            self._graph.makeinclist()
-        return self._graph.enlist[self]
+	def inclist(self):
+		"""
+		Returns the list of edges incident with vertex <self>.
+		"""
+		if not self._graph.enlist:
+			self._graph.makeinclist()
+		return self._graph.enlist[self]
 
[…]

### 2015-04-07 colorRefinement.py

@@ -199,6 +199,8 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 	for tuple in undecided:
 		first = tuple[0]
 		second = tuple[1]
+
+		print("Doing ", [first, second])
 		tempgraph = disjointunion(graphlist[first], graphlist[second])
 		num = countIsomorphism(tempgraph, fastrefine(tempgraph), GI_only)
 		if num > 0:
@@ -271,6 +273,8 @@ def countIsomorphism(graph, hasColordict=False, GI_only=False):
 			num += countIsomorphism(graph2, colordict2, GI_only)
 	return num
 
+	return 0
+
 
 def applycolors(colordict):
 	for color in colordict.keys():
@@ -300,7 +304,7 @@ def splitColorDict(colordict, g):
 						split[partitions.index(e)][key] = [value]
 					# split[partitions.index(e)].append(value.colornum)
 					split2[partitions.index(e)].append((value.colornum, value))
-	# print('split', split)
+	#print('split', split)
 	return split, split2
 
 
@@ -402,6 +406,23 @@ def comparepreproc(graphlisturl, GI_only=False):
 	elapsed_time = time.clock() - start_time
 	print('Preprocessing: {0:.4f} sec'.format(elapsed_time))
 	return compare(gs=graphlist[0], preproc=True, GI_only=True)
+
+
+def connected(v, ncomponents):
+	for vertex in v.nbs():
+		vertex.visited = True
+		vertex.component = ncomponents
+		connected(vertex)
+
+
+def findcomponents(g):
+	ncomponents = 0
+	for vertex in g.V():
+		if not vertex.visited:
+			vertex.visited = True
+			ncomponents += 1
+			vertex.component = ncomponents
+			connected(vertex, ncomponents)
 
 
 start_time = time.clock()

### 2015-04-07 colorRefinement.py
tests gemaakt en onnodige prints weg, code is nu klaar om in geleverd te worden. als we nog tijd over hebben kunnen we nog ff wat onnodige variabelen weg gooien die wat dieper in de code zitten.

@@ -67,54 +67,6 @@ def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
 	return colordict
 
 
-def fastrefine2(g, colordictarg=-1, startcolor=-1, preproc=False):
-	# initialize
-	if colordictarg == -1:
-		colordict = degcolordict(g)
-	else:
-		colordict = colordictarg
-
-	done = False
-	counter = 0
-	while not done:
-		done = True
-		counter += 1
-		if counter % 100 == 0:
-			print(counter)
-		tempcolordict = dict()
-
-		for key in colordict.keys():
-			nextcolor = max(colordict.keys()) + 1
-			buren = tuple()
-			for value in colordict[key]:
-				nc = sorted(tuple(getNeighbourColors(value)))
-				if len(buren) == 0:
-					buren = nc
-
-				if buren != nc:
-					done = False
-					if nextcolor in tempcolordict:
-						tempcolordict[nextcolor].append(value)
-					else:
-						tempcolordict[nextcolor] = [value]
-
-				else:
-					if key in tempcolordict:
-						tempcolordict[key].append(value)
-					else:
-						tempcolordict[key] = [value]
-
-		colordict = tempcolordict.copy()
-
-		for key in colordict.keys():
-			for value in colordict[key]:
-				value.colornum = key
-
-	finalcolors = []
-	for node in g.V():
-		finalcolors.append(node.colornum)
-	return colordict
-
 def degcolordict(g):
 	colordict = {}  # dictionary with key=c and value=vertex array
 	for v in g.V():
@@ -146,7 +98,7 @@ def getNeighbourColors(v):
 
 
 def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
-	assert graphlisturl != -1 or gs != -1
+	print('Now comparing graphs in graphlist ', graphlisturl)
 
 	if gs is -1:
 		graphlist = loadgraph(graphlisturl, readlist=True)[0]
@@ -166,7 +118,6 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 	else:
 		colordict = fastrefine(g)
 	graphcolors = splitColorDict(colordict, g)[0]  # is a list of colordicts
-	print(graphcolors)
 	isomorphisms = []
 	undecided = []
 
@@ -185,16 +136,6 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 						undecided.append([i, j])
[…]

### 2015-04-07 paper/paper.tex
paper updates
Merge branch 'devnew' of C:\Users\Jeroen\Projects\PycharmProjects\Graph-Isomorphism with conflicts.

--- 2015-04-07 paper/paper.tex
@@
 cycles175 & 69.8579 & 70.8041 sec \\
-bigtrees3 & -1 & -1\\
+bigtrees3 & 8.2151 & 2.5008\\
 cubes6 & -1 & -1\\
@@
 
+\section{Table with computation times}
+\begin{tabular}{c|c|c|c}
+Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
+\hline
+cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
+hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
+cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
+bigtrees3 & 8.2724 sec & 2.8264 & 0.0499 sec\\
+cubes6 & -1 & -1\\
+products72 & -1 & -1\\
+torus72 & -1 & -1\\
+\end{tabular}
+
 \end{appendices}

### 2015-04-07 colorRefinement.py

@@ -199,6 +199,8 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 	for tuple in undecided:
 		first = tuple[0]
 		second = tuple[1]
+
+		print("Doing ", [first, second])
 		tempgraph = disjointunion(graphlist[first], graphlist[second])
 		num = countIsomorphism(tempgraph, fastrefine(tempgraph), GI_only)
 		if num > 0:
@@ -237,7 +239,7 @@ def countIsomorphism(graph, hasColordict=False, GI_only=False):
 			return 0
 		# if length == 2:
 		# if int(colordict[c][0].__repr__()) <= int(graph.subgraphs[0]) < int(colordict[c][1].__repr__()):
-		# pass
+		# 		pass
 		# 	else:
 		# 		return 0
 	if isomorphism:
@@ -271,6 +273,8 @@ def countIsomorphism(graph, hasColordict=False, GI_only=False):
 			num += countIsomorphism(graph2, colordict2, GI_only)
 	return num
 
+	return 0
+
 
 def applycolors(colordict):
 	for color in colordict.keys():
@@ -300,7 +304,7 @@ def splitColorDict(colordict, g):
 						split[partitions.index(e)][key] = [value]
 					# split[partitions.index(e)].append(value.colornum)
 					split2[partitions.index(e)].append((value.colornum, value))
-	# print('split', split)
+	#print('split', split)
 	return split, split2
 
 
@@ -401,19 +405,19 @@ def comparepreproc(graphlisturl, GI_only=False):
 	print('number of twins:', nfalsetwins, ntwins)
 	elapsed_time = time.clock() - start_time
 	print('Preprocessing: {0:.4f} sec'.format(elapsed_time))
+	#return 1
 	return compare(gs=graphlist[0], preproc=True, GI_only=True)
 
 
+
+
 start_time = time.clock()
-
-compare("GI_TestInstancesWeek1/products72.grl", False)  # #aut for product72
-compare("GI_TestInstancesWeek1/torus72.grl", False)  # #aut for torus72
-compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
-compare("GI_TestInstancesWeek1/bigtrees3.grl", True)  # GI for bigtrees3
-
-comparepreproc("GI_TestInstancesWeek1/cographs1.grl")  # GI for cographs1 with preprocessing
[…]

### 2015-04-07 colorRefinement.py
component

@@ -326,6 +326,7 @@ def comparepreproc(graphlisturl, GI_only=False):
 	ngraphs = len(graphlist[0])
 	nfalsetwins, ntwins = [None] * ngraphs, [None] * ngraphs
 	for i in range(ngraphs):
+		print(findcomponents(graphlist[0][1]))
 		graphlist[0][i], nfalsetwins[i], ntwins[i] = preprocessing(graphlist[0][i])
 	print('number of twins:', nfalsetwins, ntwins)
 	elapsed_time = time.clock() - start_time
@@ -337,7 +338,7 @@ def connected(v, ncomponents):
 	for vertex in v.nbs():
 		vertex.visited = True
 		vertex.component = ncomponents
-		connected(vertex)
+		connected(vertex, ncomponents)
 
 
 def findcomponents(g):
@@ -348,17 +349,20 @@ def findcomponents(g):
 			ncomponents += 1
 			vertex.component = ncomponents
 			connected(vertex, ncomponents)
+	return ncomponents
 
 
 start_time = time.clock()
 
-compare("GI_TestInstancesWeek1/products72.grl", False)  # #aut for product72
-compare("GI_TestInstancesWeek1/torus72.grl", False)  # #aut for torus72
-compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
-compare("GI_TestInstancesWeek1/bigtrees3.grl", True)  # GI for bigtrees3
-
+# compare("GI_TestInstancesWeek1/products72.grl", False)  # #aut for product72
+# compare("GI_TestInstancesWeek1/torus72.grl", False)  # #aut for torus72
+# compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
+# compare("GI_TestInstancesWeek1/bigtrees3.grl", True)  # GI for bigtrees3
+#
 comparepreproc("GI_TestInstancesWeek1/cographs1.grl")  # GI for cographs1 with preprocessing
-comparepreproc("GI_TestInstancesWeek1/bigtrees3.grl")  # GI for cographs1 with preprocessing
+# comparepreproc("GI_TestInstancesWeek1/bigtrees3.grl")  # GI for cographs1 with preprocessing
+
+
 
 elapsed_time = time.clock() - start_time
 print('Time: {0:.4f} sec'.format(elapsed_time))

### 2015-04-07 colorRefinement.py
component

@@ -326,7 +326,7 @@ def comparepreproc(graphlisturl, GI_only=False):
 	ngraphs = len(graphlist[0])
 	nfalsetwins, ntwins = [None] * ngraphs, [None] * ngraphs
 	for i in range(ngraphs):
-		print(findcomponents(graphlist[0][1]))
+		# print(findcomponents(graphlist[0][1]))
 		graphlist[0][i], nfalsetwins[i], ntwins[i] = preprocessing(graphlist[0][i])
 	print('number of twins:', nfalsetwins, ntwins)
 	elapsed_time = time.clock() - start_time

### 2015-04-07 colorRefinement.py
.

@@ -354,13 +354,13 @@ def findcomponents(g):
 
 start_time = time.clock()
 
-# compare("GI_TestInstancesWeek1/products72.grl", False)  # #aut for product72
-# compare("GI_TestInstancesWeek1/torus72.grl", False)  # #aut for torus72
-# compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
-# compare("GI_TestInstancesWeek1/bigtrees3.grl", True)  # GI for bigtrees3
-#
+compare("GI_TestInstancesWeek1/products72.grl", False)  # #aut for product72
+compare("GI_TestInstancesWeek1/torus72.grl", False)  # #aut for torus72
+compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
+compare("GI_TestInstancesWeek1/bigtrees3.grl", True)  # GI for bigtrees3
+
 comparepreproc("GI_TestInstancesWeek1/cographs1.grl")  # GI for cographs1 with preprocessing
-# comparepreproc("GI_TestInstancesWeek1/bigtrees3.grl")  # GI for cographs1 with preprocessing
+comparepreproc("GI_TestInstancesWeek1/bigtrees3.grl")  # GI for cographs1 with preprocessing
 
 
 

### 2015-04-07 paper/paper.tex
Results table lolololololol :D

--- 2015-04-07 paper/paper.tex
@@
 \usepackage[toc,page]{appendix} % appendix
+
+\usepackage{array}
+\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
 
@@
 %------------------------------------------------
-\section{Computational Experiments}
-
-Computational Experiments here\\
-Setup good experiments beforehand and test extensively
-
-%------------------------------------------------
 \section{Results}
@@
 
+\section{Table with computation times}
+\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
+Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
+\hline
+cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
+hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
+cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
+bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
+cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
+products72 & 5.0530 sec & 5.4318 sec & 0.0207 sec\\
+torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
+\end{tabular}
 \end{appendices}

### 2015-04-07 basicgraphs.py
component

@@ -161,6 +161,7 @@ class graph():
 		self.enlist = []
 		self.colordict = -1
 		self.vertexreprmap = dict()
+		self.component = 0
 		for v in self._V:
 			self.vertexreprmap[v.__repr__()] = v
 
@@ -271,6 +272,12 @@ class graph():
 		self._E.append(e)
 		self.enlist = []
 		return e
+
+	def addedgeobject(self, eobject):
+		self._E.append(eobject)
+		self.enlist = []
+		return eobject
+
 
 	def findedge(self, u, v):
 		"""

### 2015-04-07 colorRefinement.py

@@ -5,6 +5,7 @@ import copy
 
 from makegraphs import disjointunion
 from graphIO import *
+from basicgraphs import graph
 
 
 def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
@@ -334,11 +335,12 @@ def comparepreproc(graphlisturl, GI_only=False):
 	return compare(gs=graphlist[0], preproc=True, GI_only=True)
 
 
-def connected(v, ncomponents):
+def connected(v, ncomponents, g):
 	for vertex in v.nbs():
-		vertex.visited = True
-		vertex.component = ncomponents
-		connected(vertex, ncomponents)
+		if not vertex.visited:
+			vertex.visited = True
+			vertex.component = ncomponents
+			connected(vertex, ncomponents, g)
 
 
 def findcomponents(g):
@@ -348,20 +350,44 @@ def findcomponents(g):
 			vertex.visited = True
 			ncomponents += 1
 			vertex.component = ncomponents
-			connected(vertex, ncomponents)
+			connected(vertex, ncomponents, g)
 	return ncomponents
 
 
+def componentgraphs(graphlisturl):
+	start_time = time.clock()
+	global graphlist
+	graphlist = loadgraph(graphlisturl, readlist=True)
+	ngraphs = len(graphlist[0])
+	for i in range(ngraphs - 1):
+		ncomponents = findcomponents(graphlist[0][i])
+		g = graphlist[0][i]
+		if ncomponents > 1:
+			graphs = []
+			for component in range(ncomponents):
+				graphs.append(graph())
+				for vertex in g.V():
+					if vertex.component == component:
+						graphs[component - 1].addvertexobject(vertex)
+						for edge in vertex.inclist():
+							if edge not in graphs[component - 1].E():
+								graphs[component - 1].addedgeobject(edge)
+		for j in range(ncomponents):
+			print(i, j, graphs)
+	elapsed_time = time.clock() - start_time
+	print('Components: {0:.4f} sec'.format(elapsed_time))
+
 start_time = time.clock()
 
-compare("GI_TestInstancesWeek1/products72.grl", False)  # #aut for product72
-compare("GI_TestInstancesWeek1/torus72.grl", False)  # #aut for torus72
-compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
[…]

### 2015-04-07 colorRefinement.py
component

@@ -358,22 +358,32 @@ def componentgraphs(graphlisturl):
 	start_time = time.clock()
 	global graphlist
 	graphlist = loadgraph(graphlisturl, readlist=True)
+	print(graphlist)
 	ngraphs = len(graphlist[0])
-	for i in range(ngraphs - 1):
+	subgraphlist = []
+	for i in range(ngraphs):
 		ncomponents = findcomponents(graphlist[0][i])
+		if i > 0:
+			mincomponents = min(mincomponents, ncomponents)
+		else:
+			mincomponents = ncomponents
 		g = graphlist[0][i]
 		if ncomponents > 1:
 			graphs = []
-			for component in range(ncomponents):
-				graphs.append(graph())
+			for component in range(ncomponents + 1):
+				if component != ncomponents:
+					graphs.append(graph())
 				for vertex in g.V():
 					if vertex.component == component:
 						graphs[component - 1].addvertexobject(vertex)
 						for edge in vertex.inclist():
 							if edge not in graphs[component - 1].E():
 								graphs[component - 1].addedgeobject(edge)
-		for j in range(ncomponents):
-			print(i, j, graphs)
+		subgraphlist.append(graphs)
+	# print(subgraphlist[2])
+
+
+
 	elapsed_time = time.clock() - start_time
 	print('Components: {0:.4f} sec'.format(elapsed_time))
 
@@ -384,8 +394,8 @@ start_time = time.clock()
 # compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
 # compare("GI_TestInstancesWeek1/bigtrees3.grl", True)  # GI for bigtrees3
 #
-comparepreproc("GI_TestInstancesWeek1/cographs1.grl")  # GI for cographs1 with preprocessing
-# comparepreproc("GI_TestInstancesWeek1/bigtrees3.grl")  # GI for cographs1 with preprocessing
+# comparepreproc("GI_TestInstancesWeek1/cographs1.grl")  # GI for cographs1 with preprocessing
+#comparepreproc("GI_TestInstancesWeek1/products72.grl")  # GI for cographs1 with preprocessing
 
 componentgraphs("GI_TestInstancesWeek1/cographs1.grl")
 

### 2015-04-07 paper/paper.tex
Results table lolololololol2 :D

@@
 cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
-products72 & 5.0530 sec & 5.4318 sec & 0.0207 sec\\
+products72 & 7.5950 sec & 7.5198 sec & 0.0275 sec\\
 torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\

### 2015-04-07 paper/paper.tex
paper updates

--- 2015-04-07 paper/paper.tex
@@
 
-Results here
+The results of the experiment are shown in Table \ref{table:results}.
+Seven sets of graphs were tested for isomorphisms, and three cases the computation times are significantly different.
+In the other cases, the difference in computation time is not obviously related to the preprocessing time, as the preprocessing time is not equal to the difference in computation times.
+This is most likely due to the circumstances of both executions of the algorithms did not occur under the exact same circumstances, as it was impossible to ensure the conditions were the same.
+
+Due to the rather large difference in computation times relative to the preprocessing time, only significant differences in computation time will be used as indication of increase or decrease in speed.
 
@@
 
-Conclusions here \\
-Is it faster?
+In three of the seven test cases, the computation time increased significantly. In the other four, no significant difference in the computation times was found.
+
+From this, it can be concluded that using preprocessing methods does indeed reduce the computation time needed to find graph isomorphisms.
 
@@
 \section{Table with computation times}
+\begin{table}[h]
 \begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
@@
 \end{tabular}
+\caption{Table showing the result from the experiment. For each graph, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
+\label{table:results}
+\end{table}
 \end{appendices}

### 2015-04-07 paper/paper.tex
component

--- 2015-04-07 paper/paper.tex
@@
 Seven sets of graphs were tested for isomorphisms, and three cases the computation times are significantly different.
-In the other cases, the difference in computation time is not obviously related to the preprocessing time, as the preprocessing time is not equal to the difference in computation times.
+In the other cases, the preprocessing time is relatively very small.
+This is because the low complexity of \emph{gettwins} and the fact that \emph{preprocessing} does nothing when there are no (false) twins.
+The difference in computation time is not obviously related to the preprocessing time, as the preprocessing time is not equal to the difference in computation times.
 This is most likely due to the circumstances of both executions of the algorithms did not occur under the exact same circumstances, as it was impossible to ensure the conditions were the same.
@@
 \end{tabular}
-\caption{Table showing the result from the experiment. For each graph, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
+\caption{Table showing the result from the experiment.
+For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
 \label{table:results}

### 2015-04-07 paper/paper.tex
paper updates
component

@@
 The algorithm is divided into two subalgorithms.
-The subalgorithm \textit{gettwins} finds all twins and false twins and the subalgorithm \textit{preprocessing} replaces each (false) twin by a single colored vertex as described above.
+The subalgorithm \emph{gettwins} finds all twins and false twins and the subalgorithm \emph{preprocessing} replaces each (false) twin by a single colored vertex as described above.
 In the following subsections these algorithms and their worst case time complexities will be analyzed.

### 2015-04-07 colorRefinement.py
shit.. werkt niet

@@ -148,7 +148,7 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 
 	printresult(isomorphisms)
 
-	return colordict
+	return len(isomorphisms)
 
 
 def printresult(isomorphims):
@@ -314,7 +314,7 @@ def preprocessing(g):
 			twin[0].colornum = -twin[0].twinsize - mx
 		for i, twin in enumerate(falsetwins + twins):
 			for j in combined[i]:
-				if j in g.V() and twin[0] != j and not g.findedge(twin[0],j):
+				if j in g.V() and twin[0] != j and not g.findedge(twin[0], j):
 					g.addedge(twin[0], j)
 		g._V.sort(key=lambda x: x._label)
 	return g, lftwins, ltwins
@@ -331,8 +331,7 @@ def comparepreproc(graphlisturl, GI_only=False):
 	print('number of twins:', nfalsetwins, ntwins)
 	elapsed_time = time.clock() - start_time
 	print('Preprocessing: {0:.4f} sec'.format(elapsed_time))
-	nvertices = len(graphlist[0][0].V())
-	return nvertices  # compare(gs=graphlist[0], preproc=True, GI_only=True)
+	return compare(gs=graphlist[0], preproc=True, GI_only=True)
 
 
 def connected(v, ncomponents, g):
@@ -358,7 +357,6 @@ def componentgraphs(graphlisturl):
 	start_time = time.clock()
 	global graphlist
 	graphlist = loadgraph(graphlisturl, readlist=True)
-	print(graphlist)
 	ngraphs = len(graphlist[0])
 	subgraphlist = []
 	for i in range(ngraphs):
@@ -375,10 +373,60 @@ def componentgraphs(graphlisturl):
 						if edge not in graphs[component - 1].E():
 							graphs[component - 1].addedgeobject(edge)
 		subgraphlist.append(graphs)
+	return subgraphlist
 	# print(subgraphlist[2])
+
+def componentpreproc(graphlisturl):
+	grl = componentgraphs(graphlisturl)
+
+	colordicts = []
+	for componentlist in grl:
+		tempcolordicts = []
+		for component in componentlist:
+			tempcolordicts.append(fastrefine(component))
+		colordicts.append(tempcolordicts)
+
+	print(colordicts)
+	colordicts2 = copy.deepcopy(colordicts)
[…]

### 2015-04-07 basicgraphs.py
imports weg gehaald en vervangen

@@ -164,6 +164,19 @@ class graph():
 		for v in self._V:
 			self.vertexreprmap[v.__repr__()] = v
 
+	def getcopy(self):
+		g = graph()
+		g._V = self._V
+		g._E = self._E
+		g._directed = self._directed
+		g.subgraphs = self.subgraphs
+		g._simple = self._simple
+		g._nextlabel = self._nextlabel
+		g.enlist = self.enlist
+		g.colordict = self.colordict
+		g.vertexreprmap = self.vertexreprmap
+		return g
+
 	def getvertexbyrepr(self, repr):
 		if not self.vertexreprmap:
 			for v in self._V:

### 2015-04-07 colorRefinement.py

@@ -1,7 +1,6 @@
 __author__ = 'Tim (& [Jeroen])'
 
 import time
-import copy
 
 from makegraphs import disjointunion
 from graphIO import *
@@ -195,7 +194,7 @@ def countIsomorphism(graph, hasColordict=False, GI_only=False):
 			colordict[newcolor].append(y)
 
 			applycolors(colordict)
-			graph2 = copy.deepcopy(graph)
+			graph2 = graph.getcopy()
 			graph2.generatecolordict()
 			colordict2 = graph2.getcolordict()
 

### 2015-04-07 paper/paper.tex
proof poging

@@
 Let $G = (V,E)$ be a graph.
-Two vertices $u, v \in V$ are \emph{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash {v} = N(v)\textbackslash {u}$.
+Two vertices $u, v \in V$ are \emph{twins} if $\{u,v\} \in E$ and $N(u)\textbackslash \{v\} = N(v)\textbackslash \{u\}$.
 \end{definition}
@@
 \begin{compactenum}
-\item Twins have the same color $\iff$ Twins have the same size (number of vertices).
-\item False twins have the same color $\iff$ False twins have the same size (number of vertices).
-\item A twin and a false twin can't have the same color.
+\item Vertices in the new graph have the same color $\iff$ The corresponding twinsets or false twinsets in the old graph have the same size (number of vertices).
+\item Two vertices in the new graph can't have the same color if one of them corresponds to a twinset and the other one two a false twinset in the old graph.
 \end{compactenum}
@@
 If there are any twins all edges with a head or tail in one of these twins will be deleted.
-The complexity of this is $O(m +$ number of vertices (\emph{twins}+\emph{falsetwins}))$ < O (nm)$.
+The complexity of this is $O(m +$ number of vertices in (\emph{twins}+\emph{falsetwins}))$ < O (nm)$.
 Then in line 13-19 all vertices which are in twins or falsetwins will be removed.
@@
 \begin{theorem}
-Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs where each vertex has the same color and let $H_1 = (V_1, E_1)$ and $H_2 = (V_2, E_2)$ be resp.
+Let $G_1 = (V_{G1}, E_{G1})$ and $G_2 = (V_{G2}, E_{G2})$ be two undirected colored graphs where each vertex has color 0 and let $H_1 = (V_{H1}, E_{H1})$ and $H_2 = (V_{H2}, E_{H2})$ be resp.
 the same graphs as $G_1$ and $G_2$ where each (false) twin is replaced by a colored vertex such that: \begin{compactenum}[\upshape(a)]
-\item Twins (False twins) have the same color $\iff$ Twins (False twins) have the same size (number of vertices).
-\item A twin and a false twin can't have the same color.
+\item Vertices in $H_1$ ($H_2$) have the same color $\iff$ The corresponding twinsets or false twinsets in $G_1$ ($G_2$) have the same size (number of vertices).
+\item Two vertices in $H_1$ ($H_2$) can't have the same color if one of them corresponds to a twinset in $G_1$ ($G_2$) and the other one corresponds to a false twinset in $G_1$ ($G_2$).
+They also can't have color 0.
 \end{compactenum}
@@
 \begin{proof}
-Todo
+$\Leftarrow$:  $\exists$ graph isomorphism $h: H_1 \to H_2$.
+We want to proof that $g: G_1 \to G_2$ is a graph isomorphism.
+If $v \in V_{H1}$ has color 0 we define $g(v) = h(v)$.
+If $v \in V_{H1}$ has color $\neq$ 0, $\exists$ $ w \in V_{H2}$ such that color($v$) = color($w$) (since $H_1$ and $H_2$ are isomorphs).
+$v$ and $w$ either have resp.
+corresponding false twinsets \emph{ftw} $\subseteq V_{G1}$ and \emph{ftw2} $\subseteq V_{G2}$ or they have resp.
+corresponding twinsets \emph{tw} $\subseteq V_{G1}$ and \emph{tw2} $\subseteq V_{G2}$.
+In the first case map each $x \in$ \emph{ftw} to a different $y \in$ \emph{ftw2}.
+Since they are false twins it doesn't matter which $x$ is mapped to which $y$.
+
+Similar for twins
+
 \end{proof}
@@
 \end{table}
+
+\section{Complexity}
+\begin{table}[h]
+\begin{tabular}{c|c}
+n & time \\
+\hline
+34 & 0.0017\\
+66 & 0.0032\\
+130 & 0.0071\\
+258 & 0.161\\
+514 & 0.0344\\
+1026 & 0.0805\\
+2050 & 0.2019\\
+4098 & 0.5874\\
+8194 & 2.7102
+
+\end{tabular}
+\caption{Table showing the result from the experiment.
+For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
+\label{table:results}
+\end{table}
 \end{appendices}

### 2015-04-07 paper/paper.tex
New test results

--- 2015-04-07 paper/paper.tex
@@
 The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code.
-The python interpreter used was Python 3.4 and the laptop was running Windows 8.1 at the time of the testing.
+The python interpreter used was Python 3.4 and the laptop was running Windows 10 Pro Technical Preview (at 3.5 GHz and 8.00 GB) at the time of the testing.
 Efforts were made to ensure all the testing was performed under the same circumstances.
@@
 \hline
-cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
-hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
-cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
-bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
-cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
-products72 & 7.5950 sec & 7.5198 sec & 0.0275 sec\\
-torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
+cographs1 & 6.6017 sec & 0.0048 sec & 0.0027 sec \\
+hugecographs & >30 min & 29.8713 sec & 0.0214 sec \\
+cycles175 & 13.7522 sec & 13.9265 sec & 0.0238 sec\\
+bigtrees3 & 0.9652 sec & 0.2700 sec & 0.0323 sec\\
+cubes6 & 0.5967 sec & 0.5877 sec & 0.0072 sec\\
+products72 & 0.6083 sec & 0.6353 sec & 0.0123 sec\\
+torus72 & 3.5590 sec & 3.6059 sec & 0.0106 sec\\
+\end{tabular}
+\caption{Table showing the result from the experiment.
+For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
+\label{table:results}
+\end{table}
+
+\section{Complexity}
+\begin{table}[h]
+\begin{tabular}{c|c}
+n & time \\
+\hline
+34 & 0.0017\\
+66 & 0.0032\\
+130 & 0.0071\\
+258 & 0.161\\
+514 & 0.0344\\
+1026 & 0.0805\\
+2050 & 0.2019\\
+4098 & 0.5874\\
+8194 & 2.7102
+
 \end{tabular}

### 2015-04-07 paper/paper.tex

--- 2015-04-07 paper/paper.tex
@@
 \hline
-cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
-hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
-cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
-bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
-cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
-products72 & 7.5950 sec & 7.5198 sec & 0.0275 sec\\
-torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
+cographs1 & 6.6017 sec & 0.0048 sec & 0.0027 sec \\
+hugecographs & >30 min & 29.8713 sec & 0.0214 sec \\
+cycles175 & 13.7522 sec & 13.9265 sec & 0.0238 sec\\
+bigtrees3 & 0.9652 sec & 0.2700 sec & 0.0323 sec\\
+cubes6 & 0.5967 sec & 0.5877 sec & 0.0072 sec\\
+products72 & 0.6083 sec & 0.6353 sec & 0.0123 sec\\
+torus72 & 3.5590 sec & 3.6059 sec & 0.0106 sec\\
 \end{tabular}

### 2015-04-07 paper/paper.tex
Fixed GHz thing in paper :D

@@
 The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code.
-The python interpreter used was Python 3.4 and the laptop was running Windows 10 Pro Technical Preview (at 3.5 GHz and 8.00 GB) at the time of the testing.
+The python interpreter used was Python 3.4 and the laptop was running Windows 10 Pro Technical Preview (at 3.75 GHz (average speed, max 3.9 GHz) and 8.00 GB) at the time of the testing.
 Efforts were made to ensure all the testing was performed under the same circumstances.

### 2015-04-08 paper/paper.tex
New test results

--- 2015-04-07 paper/paper.tex
@@
 \subsection{Experiment Setup}
-For the testing, a single laptop was used to collect all the timed data.
+For the testing, a single computer was used to collect all the timed data.
 The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code.
-The python interpreter used was Python 3.4 and the laptop was running Windows 10 Pro Technical Preview (at 3.5 GHz and 8.00 GB) at the time of the testing.
+The python interpreter used was Python 3.4 and the computer was running Windows 10 Pro Technical Preview (at 3.75 GHz (average speed, max 3.9 GHz) and 8.00 GB) at the time of the testing.
 Efforts were made to ensure all the testing was performed under the same circumstances.
@@
 cographs1 & 6.6017 sec & 0.0048 sec & 0.0027 sec \\
-hugecographs & >30 min & 29.8713 sec & 0.0214 sec \\
+hugecographs & >7 hours & 29.8713 sec & 0.0214 sec \\
 cycles175 & 13.7522 sec & 13.9265 sec & 0.0238 sec\\

### 2015-04-08 colorRefinement.py
.

@@ -98,6 +98,8 @@ def getNeighbourColors(v):
 
 def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 	print('Now comparing graphs in graphlist ', graphlisturl)
+	if graphlisturl.endswith('.gr'):
+		gs = [loadgraph(graphlisturl, readlist=False),loadgraph(graphlisturl, readlist=False)]
 
 	if gs is -1:
 		graphlist = loadgraph(graphlisturl, readlist=True)[0]
@@ -116,6 +118,9 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 		colordict = fastrefine(g, preproc=True)
 	else:
 		colordict = fastrefine(g)
+	print(colordict)
+	writeDOT(g, "GI_TestInstancesWeek1/dinges.dot")
+
 	graphcolors = splitColorDict(colordict, g)[0]  # is a list of colordicts
 	isomorphisms = []
 	undecided = []
@@ -353,13 +358,20 @@ def findcomponents(g):
 
 start_time = time.clock()
 
-compare("GI_TestInstancesWeek1/products72.grl", False)  # #aut for product72
-compare("GI_TestInstancesWeek1/torus72.grl", False)  # #aut for torus72
-compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
-compare("GI_TestInstancesWeek1/bigtrees3.grl", True)  # GI for bigtrees3
 
-comparepreproc("GI_TestInstancesWeek1/cographs1.grl")  # GI for cographs1 with preprocessing
-comparepreproc("GI_TestInstancesWeek1/bigtrees3.grl")  # GI for cographs1 with preprocessing
+# compare("GI_TestInstancesWeek1/basicAut1.gr", False)  # #aut for product72
+compare("GI_TestInstancesWeek1/basicAut2.gr", False)  # #aut for product72
+# compare("GI_TestInstancesWeek1/basicGI1.grl", True)  # #aut for product72
+# compare("GI_TestInstancesWeek1/basicGI2.grl", True)  # #aut for product72
+# compare("GI_TestInstancesWeek1/basicGI3.grl", True)  # #aut for product72
+# compare("GI_TestInstancesWeek1/basicGIAut.grl", True)  # #aut for product72
+# compare("GI_TestInstancesWeek1/basicGIAut.grl", False)  # #aut for product72
[…]

### 2015-04-08 colorRefinement.py
alles werkt nu eindelijk ...

@@ -6,7 +6,7 @@ from makegraphs import disjointunion
 from graphIO import *
 
 
-def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
+def fastrefine2(g, colordictarg=-1, startcolor=-1, preproc=False):
 	if colordictarg is -1:
 		if g.colordict == -1:
 			if not preproc:
@@ -66,6 +66,52 @@ def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
 	return colordict
 
 
+def fastrefine(g, colordictarg=-1, startcolor=-1, preproc=False):
+	# initialize
+	if colordictarg == -1:
+		colordict = degcolordict(g)
+	else:
+		colordict = colordictarg
+
+	done = False
+	while not done:
+		done = True
+		tempcolordict = dict()
+
+		for key in colordict.keys():
+			nextcolor = max(colordict.keys()) + 1
+			buren = tuple()
+			for value in colordict[key]:
+				nc = sorted(tuple(getNeighbourColors(value)))
+				if len(buren) == 0:
+					buren = nc
+
+				if buren != nc:
+					done = False
+					if nextcolor in tempcolordict:
+						tempcolordict[nextcolor].append(value)
+					else:
+						tempcolordict[nextcolor] = [value]
+
+				else:
+					if key in tempcolordict:
+						tempcolordict[key].append(value)
+					else:
+						tempcolordict[key] = [value]
+
+		colordict = tempcolordict.copy()
+
+		for key in colordict.keys():
+			for value in colordict[key]:
+				value.colornum = key
+
+	finalcolors = []
+	for node in g.V():
+		finalcolors.append(node.colornum)
+
+	return colordict
+
+
 def degcolordict(g):
 	colordict = {}  # dictionary with key=c and value=vertex array
 	for v in g.V():
@@ -99,8 +145,8 @@ def getNeighbourColors(v):
 def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 	print('Now comparing graphs in graphlist ', graphlisturl)
 	if graphlisturl.endswith('.gr'):
-		gs = [loadgraph(graphlisturl, readlist=False),loadgraph(graphlisturl, readlist=False)]
-
+		gs = [loadgraph(graphlisturl, readlist=False), loadgraph(graphlisturl, readlist=False)]
[…]

### 2015-04-08 colorRefinement.py
ready for hand in

@@ -146,7 +146,6 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 	print('Now comparing graphs in graphlist ', graphlisturl)
 	if graphlisturl.endswith('.gr'):
 		gs = [loadgraph(graphlisturl, readlist=False), loadgraph(graphlisturl, readlist=False)]
-	print('cc', fastrefine(loadgraph(graphlisturl, readlist=False)))
 	if gs is -1:
 		graphlist = loadgraph(graphlisturl, readlist=True)[0]
 	else:
@@ -407,7 +406,7 @@ def findcomponents(g):
 
 start_time = time.clock()
 
-
+# instances from the delivery
 # compare("GI_TestInstancesWeek1/basicAut1.gr", False)  # #aut for product72
 # compare("GI_TestInstancesWeek1/basicAut2.gr", False)  # #aut for product72
 # compare("GI_TestInstancesWeek1/basicGI1.grl", True)  # #aut for product72
@@ -416,10 +415,13 @@ start_time = time.clock()
 # compare("GI_TestInstancesWeek1/basicGIAut.grl", True)  # #aut for product72
 # compare("GI_TestInstancesWeek1/basicGIAut.grl", False)  # #aut for product72
 
+# instances from before delivery (the hand in pdf)
+# compare("GI_TestInstancesWeek1/products72.grl", False)  # #aut for product72
 # compare("GI_TestInstancesWeek1/torus72.grl", False)  # #aut for torus72
 # compare("GI_TestInstancesWeek1/cubes6.grl", True)  # GI for cubes6
 # compare("GI_TestInstancesWeek1/bigtrees3.grl", True)  # GI for bigtrees3
-#
+
+# extra instances for twins
 # comparepreproc("GI_TestInstancesWeek1/cographs1.grl")  # GI for cographs1 with preprocessing
 # comparepreproc("GI_TestInstancesWeek1/bigtrees3.grl")  # GI for cographs1 with preprocessing
 

### 2015-04-08 colorRefinement.py
idk what changed

@@ -144,7 +144,7 @@ def getNeighbourColors(v):
 
 def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 	print('Now comparing graphs in graphlist ', graphlisturl)
-	if graphlisturl.endswith('.gr'):
+	if not preproc and graphlisturl.endswith('.gr'):
 		gs = [loadgraph(graphlisturl, readlist=False), loadgraph(graphlisturl, readlist=False)]
 	if gs is -1:
 		graphlist = loadgraph(graphlisturl, readlist=True)[0]
@@ -195,7 +195,7 @@ def compare(graphlisturl=-1, GI_only=False, gs=-1, preproc=False):
 
 	printresult(isomorphisms)
 
-	return colordict
+	return
 
 
 def printresult(isomorphims):

### 2015-04-08 paper/paper.tex
proof

@@
 \section{Proof of Correctness}
-NOG NIET AF!
 \begin{definition}
@@
 \end{definition}
+\begin{definition}\label{def:iso}
+Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected graphs. A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if:
+\begin{compactenum}[\upshape(a)]
+\item $f$ is a bijection. \label{voorwaarde1}
+\item $\forall a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$.
+\end{compactenum}
+When such a function exists, $G_1$ and $G_2$ are called \emph{isomorphic graphs}. 
+\end{definition}
 \begin{definition}
-Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \emph{graph isomorphism} if \begin{compactenum}[\upshape(a)]
-\item $f$ is a bijection, 
-\item for all $a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$, and 
-\item $color(v)$ = $color (f(v)$. When such a function exist, $G_1$ and $G_2$ are called \emph{isomorphic graphs}. 
+Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \emph{colored graph isomorphism} if: 
+\begin{compactenum}[\upshape(a)]
+\item $f$ is a graph isomorphism.
+\item $\forall v \in V_1$: $color(v)$ = $color (f(v)$. 
 \end{compactenum}
+When such a function exists, $G_1$ and $G_2$ are called \emph{colored isomorphic graphs}. 
 \end{definition}
 \begin{theorem}
-Let $G_1 = (V_{G1}, E_{G1})$ and $G_2 = (V_{G2}, E_{G2})$ be two undirected colored graphs where each vertex has color 0 and let $H_1 = (V_{H1}, E_{H1})$ and $H_2 = (V_{H2}, E_{H2})$ be resp.
-the same graphs as $G_1$ and $G_2$ where each (false) twin is replaced by a colored vertex such that: \begin{compactenum}[\upshape(a)]
+Let $G_1 = (V_{G1}, E_{G1})$ and $G_2 = (V_{G2}, E_{G2})$ be two undirected  graphs and let $H_1 = (V_{H1}, E_{H1})$ and $H_2 = (V_{H2}, E_{H2})$ be resp.
+the same graphs as $G_1$ and $G_2$ where vertices which aren't (false) twins with any other vertex get color 0 and each (false) twin is replaced by a colored vertex such that: \begin{compactenum}[\upshape(a)]
 \item Vertices in $H_1$ ($H_2$) have the same color $\iff$ The corresponding twinsets or false twinsets in $G_1$ ($G_2$) have the same size (number of vertices).
@@
 \end{compactenum}
-Graph $G_1$ and $G_2$ are isomorphic $\iff$ Graph $H_1$ and $H_2$ are isomorphic.
+Graph $G_1$ and $G_2$ are isomorphic $\iff$ Graph $H_1$ and $H_2$ are colored isomorphic.
 \end{theorem}
 \begin{proof}
-$\Leftarrow$:  $\exists$ graph isomorphism $h: H_1 \to H_2$.
-We want to proof that $g: G_1 \to G_2$ is a graph isomorphism.
-If $v \in V_{H1}$ has color 0 we define $g(v) = h(v)$.
+$\Leftarrow$:  $\exists$ graph isomorphism $h: H_1 \to H_2$. If $v \in V_{H1}$ has color 0: we define $g(v) = h(v)$.
 If $v \in V_{H1}$ has color $\neq$ 0, $\exists$ $ w \in V_{H2}$ such that color($v$) = color($w$) (since $H_1$ and $H_2$ are isomorphs).
@@
 corresponding twinsets \emph{tw} $\subseteq V_{G1}$ and \emph{tw2} $\subseteq V_{G2}$.
-In the first case map each $x \in$ \emph{ftw} to a different $y \in$ \emph{ftw2}.
+In the first case $g$ maps each $x \in$ \emph{ftw} to a different $y \in$ \emph{ftw2}.
 Since they are false twins it doesn't matter which $x$ is mapped to which $y$.
+In the second case $g$ maps $x \in$ \emph{tw} to $y \in$ \emph{tw2} similarly.
 
-Similar for twins
+We want to prove that $g: G_1 \to G_2$ is a graph isomorphism.
+$V_{H1}$ and $V_{H2}$ have the same size and each $v_1 \in V_{H1}$ corresponds to a $v_2 \in V_{H1}$ with the same color.
+The colors of $v_1$ and $v_2$ defines the sizes of the corresponding (false) twinsets in resp.
+$G_{H1}$ and $G_{H2}$, thus $G_{H1}$ and $G_{H2}$ also have the same size.
+Since $g$ is defined such that it is an injection and $V_{G1}$ and $V_{G2}$ have the same size, $g$ is a bijection \cite{website:proofwiki}.
+Thus condition \ref{voorwaarde1} of definition \ref{def:iso} is satisfied.
+
+Define a module $M_i \subseteq V_{G1}: \{v \in V_{G1}$ $|$ corresponding vertex in $H_1$ has color $i \}$.
+$\forall a, b \in V_{G1}$ such that $a,b \in M_i$ for some $i$: $\{a,b\} \in E_{G1} \iff \{c,d\} \in E_{H1}$.
+$c,d$ are the corresponding vertices of resp.
+$a,b$.
+$\{c,d\} \in E_{H1} \iff$
+
+%$\forall a, b \in V_{G1}$ such that $a \in M_i$ and $b \in M_j$ for some $i,j: i\neq j$:
 

### 2015-04-08 colorRefinement.py
proof

@@ -439,7 +439,7 @@ start_time = time.clock()
 #comparepreproc("GI_TestInstancesWeek1/products72.grl")  # GI for cographs1 with preprocessing
 
 # componentgraphs("GI_TestInstancesWeek1/cographs1.grl")
-componentpreproc('GI_TestInstancesWeek1/crefBM_4_16.grl')
+# componentpreproc('GI_TestInstancesWeek1/crefBM_4_16.grl')
 
 elapsed_time = time.clock() - start_time
 print('Time: {0:.4f} sec'.format(elapsed_time))

### 2015-04-09 paper/paper.tex
proof

@@
 The complexity of this is $O(n^2)$.
-In line 20-28 a new colored vertex will be added for each (false) twin $(O(n)$ and finnaly the edges from these vertices will be added ($O(n^2 (n+m)$).
+In line 20-26 a new colored vertex will be added for each (false) twin $(O(n)$ and finnaly the edges from these vertices will be added ($O(n^2 (n+m)$).
 The worst case complexity of this algorithm is ($O(n^2 (n+m)$), however in average there are much less (false) twins than vertices (there are at most $n/2$).
@@
 \item $f$ is a bijection. \label{voorwaarde1}
-\item $\forall a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$.
+\item $\forall a, b \in V_1, \{a, b\} \in E_1$ if and only if $\{f(a), f(b)\} \in E_2$.\label{voorwaarde2}
 \end{compactenum}
@@
 \end{definition}
-\begin{definition}
+\begin{definition}\label{def:coloriso}
 Let $G_1 = (V_1, E_1)$ and $G_2 = (V_2, E_2)$ be two undirected colored graphs. A function $f: V_1 \to V_2$ is called a \emph{colored graph isomorphism} if: 
 \begin{compactenum}[\upshape(a)]
-\item $f$ is a graph isomorphism.
-\item $\forall v \in V_1$: $color(v)$ = $color (f(v)$. 
+\item $f$ is a graph isomorphism.\label{voorwaarde4}
+\item $\forall v \in V_1$: $color(v)$ = $color (f(v)$. \label{voorwaarde3}
 \end{compactenum}
@@
 \begin{proof}
-$\Leftarrow$:  $\exists$ graph isomorphism $h: H_1 \to H_2$. If $v \in V_{H1}$ has color 0: we define $g(v) = h(v)$.
+%We shall define $f_i$: $G_i\to H_i$ as the transformation descriped above and   and $f_i^{-1}$: $H_i\to G_i$ as the inverse of that transformation.
+Note that $f_i^{-1}$ maps a vertex with color $\neq$ 0 to a set of twins or falsetwins.
+Also w.l.o.g we assume $f$ gives color (
+
+$\Leftarrow$:  $\exists$ colored graph isomorphism $h: H_1 \to H_2$. If $v \in V_{H1}$ has color 0: we define $g(v) = h(v)$.
 If $v \in V_{H1}$ has color $\neq$ 0, $\exists$ $ w \in V_{H2}$ such that color($v$) = color($w$) (since $H_1$ and $H_2$ are isomorphs).
@@
 
-Define a module $M_i \subseteq V_{G1}: \{v \in V_{G1}$ $|$ corresponding vertex in $H_1$ has color $i \}$.
-$\forall a, b \in V_{G1}$ such that $a,b \in M_i$ for some $i$: $\{a,b\} \in E_{G1} \iff \{c,d\} \in E_{H1}$.
+Define a module $M_i \subseteq V_{G1}: \{v \in V_{G1}$ $|$ corresponding vertex in $H_1$ has color $i \}$. $\forall a, b \in V_{G1}$, $a \in M_i$ and $b$ $\in$ $M_j$ for some $i,j$: 
+\begin{compactenum}
+\item if $i = j$: $\{a,b\} \in E_{G1} \iff \{c,d\} \in E_{H1}$.
 $c,d$ are the corresponding vertices of resp.
 $a,b$.
-$\{c,d\} \in E_{H1} \iff$
+$\{c,d\} \in E_{H1} \iff \{h(c),h(d)\} \in E_{H2} \iff \{g(a),g(b)\} \in E_{G2}$, because $g(a)$ and $g(b)$ are elements of the corresponding (false) twinset of resp.
+$c$ and $d$ and all those elements have the same neighbours.
+\item if $i \neq j$: If $M_i$ is a false twin, $\{a,b\} \notin E_{G1} $ and $\{g(a),g(b)\} \in E_{G2}$.
+If $M_j$ is a twin $\{a,b\} \in E_{G1} $ and $\{g(a),g(b)\}\in E_{G2}$.
+If $i = 0$, the loop consists in $G_1 \iff$ it exists in $H_1 \iff$ it exists in $H_2 \iff$ it exists in $G_2$.
+\end{compactenum} 
+$\forall a, b \in V_{G1}, \{a, b\} \in E_{G1} \iff \{g(a), g(b)\} \in E_{G2}$.
+Thus condition \ref{voorwaarde2} of definition \ref{def:iso} is satisfied and $g$ is a graph isomorphism.
 
-%$\forall a, b \in V_{G1}$ such that $a \in M_i$ and $b \in M_j$ for some $i,j: i\neq j$:
+$\Rightarrow$: $\exists$ graph isomorphism $g: G_1 \to G_2$.
+$\forall M_i (G_1) \subseteq V_{G1}, M_i (G_2) \subseteq V_{G2}$.
+The function $h$ maps the corresponding vertex of $M_i (G_1)$ in $H_1$ to the corresponding vertex of $M_i (G_2)$ in $H_2$.
+
+We want to prove that $h: H_1 \to H_2$ is a colored graph isomorphism.
+It is defined such that it is color preserving, so condition \ref{voorwaarde3} of definition \ref{def:coloriso} is satisfied.
+For each $M_i (G_1) \subseteq V_{G1}$ $\exists$ $M_i (G_2) \subseteq V_{G2}$ with the same size and each $M_i$ in $G$ is a single vertex in $H$.
+Thus $V_{H1}$ and $V_{H2}$ have the same size (since $V_{G1}$ and $V_{G2}$ have the same size).
+Since $G_1$ and $G_2$ are isomorphic, they contain the same modules $M_i$.
+Thus $h$ can map each corresponding vertex of $M_i (G1)$ to a unique corresponding vertex of $M_i (G2)$.
+So $h$ is an injection and $V_{H1}$ and $V_{H2}$ have the same size, thus $h$ is also a bijection \cite{website:proofwiki}.
+
+$\forall a, b \in V_{H1}$: color($a$) = i, color($b$) = j, $a$ corresponds to $M_i (G_1)$ and $b$ corresponds to $M_j (G_1)$.
+If $i=j: M_i$ and $M_j$ can either be the same set of (false) twins or different sets of equal size and both twins or both false twins.
+$ \{a, b\} \in E_{H1} \iff \{c,d\} \in E_{G1}, c \in  M_i, d \in  M_j \iff \{g(c),g(d)\} \in E_{G2} \iff \{h(a),h(b)\} \in E_{H2}$.
+Because $h(a)$ and $h(b)$ corresponds to resp.
+$g(c)$ and $g(d)$.
+By definition \ref{def:iso}, $h$ is graph isomorphism.
+Condition \ref{voorwaarde4} of definition \ref{def:coloriso} is satisfied and $h$ is a colored graph isomorphism.
 
 \end{proof}
-
-%bron http://pages.cs.wisc.edu/~dieter/Papers/3gi.pdf
 
@@
 \printbibliography
+%bibliography{references}
 
@@
 		combined = falsetwinsN + twinsN
-		mx = 0
 		for i, twin in enumerate(falsetwins):
@@
 			twin[0].colornum = -twin[0].twinsize
-			mx = max(mx, len(twin))
 		for i, twin in enumerate(twins):
-			g.addvertexobject(twin[0], True, len(twin) + mx)
-			twin[0].colornum = -twin[0].twinsize - mx
+			g.addvertexobject(twin[0], True, len(twin))
+			twin[0].colornum = twin[0].twinsize
 		for i, twin in enumerate(falsetwins + twins):
@@
 130 & 0.0071\\
-258 & 0.161\\
+258 & 0.0161\\
 514 & 0.0344\\

### 2015-04-10 paper/paper.tex
proof

@@
 
-For this paper, the time complexity of the algorithms will be calculated.
-The difference in performance between the cases will be shown by computational results as well as the calculated time complexities.
+For this paper, the time complexity of the algorithms will be calculated. The difference in performance between the cases will be shown by computational results.
 
@@
 \subsection{Implementation}
-The algorithm is divided into two subalgorithms.
-The subalgorithm \emph{gettwins} finds all twins and false twins and the subalgorithm \emph{preprocessing} replaces each (false) twin by a single colored vertex as described above.
+The algorithm is divided into two subroutines.
+The subroutine \emph{gettwins} finds all twins and false twins and the subroutine \emph{preprocessing} replaces each (false) twin by a single colored vertex as described above.
 In the following subsections these algorithms and their worst case time complexities will be analyzed.
@@
 \subsubsection{Finding twins and false twins}
-The algorithm \emph{gettwins} can be found in appendix \ref{gettwins}.
+The subroutine \emph{gettwins} can be found in appendix \ref{gettwins}.
 In line 2-10 two lists, \emph{nbs} and \emph{nbs2}, are created.
@@
 Finding all the neighbours only require going though all the edges once, so the time complexity is $O(m)$.
-The sorting algorithm has time complexity $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes $O(n^2 \log n)$.
+The sorting algorithm has time complexity $O(y \log y)$, $y=$max(len($x$)), $x \in $ \emph{nbs} < $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes at most $O(n^2 \log n)$.
 
 In line 11-16 a dictionary \emph{falsetwins} is created where the keys are all the items from \emph{nbs} and the values a list of the corresponding vertices.
-Since \emph{nbs} has length $n$ and \emph{falsetwins} has at most length $n$, the time complexity of this is $O(n^2)$.
+The worst case time complexity of checking if an item is in a dictionary is $O(k+l)$ where $k$ is the number of keys and $l$ the length of the key which is a tuple.
+The average case is however only $O(l)$ \cite{website:pythonTimeComplexity}.
+$l\leq n$ and $k\leq n$, and this dictionary operation is in a for loop of length $n$, so the worst case time complexity of this is $O(n^3)$, but the average case is $O(n^2)$.
 In line 23 the items in the \emph{falsetwins} with only one vertex as value are removed.
@@
 A similar dictionary \emph{twins} is created where the keys are the items from \emph{nbs2}.
-The time complexity of \textit{gettwins} is thus $O(n^2 \log n)$.
+The worst case time complexity of \textit{gettwins} is thus $O(n^3)$.
 
@@
 If there are any twins all edges with a head or tail in one of these twins will be deleted.
-The complexity of this is $O(m +$ number of vertices in (\emph{twins}+\emph{falsetwins}))$ < O (nm)$.
+The complexity of this is $O(mv) < O (nm)$, where $v$ is the number of vertices in (\emph{twins}+\emph{falsetwins}).
 Then in line 13-19 all vertices which are in twins or falsetwins will be removed.
-The complexity of this is $O(n^2)$.
-In line 20-26 a new colored vertex will be added for each (false) twin $(O(n)$ and finnaly the edges from these vertices will be added ($O(n^2 (n+m)$).
-The worst case complexity of this algorithm is ($O(n^2 (n+m)$), however in average there are much less (false) twins than vertices (there are at most $n/2$).
-These twins also have much less than $n$ neighbours.
+The complexity of this is $O(nv) < O(n^2)$.
+In line 20-26 a new colored vertex will be added for each (false) twin $(O(n))$ and finally the edges from these vertices will be added ($O(n^2 (n+m))$).
+The worst case time complexity of this algorithm is ($O(n^2 (n+m)$), but if there are only $v$ vertices which are \emph{twins} or \emph{falsetwins} and they have maximally $w$ neighbours, the complexity is $O(vw) (n+m)$.
 
@@
 $\forall M_i (G_1) \subseteq V_{G1}, M_i (G_2) \subseteq V_{G2}$.
-The function $h$ maps the corresponding vertex of $M_i (G_1)$ in $H_1$ to the corresponding vertex of $M_i (G_2)$ in $H_2$.
+The function $h$ maps the corresponding vertex of $M_i (G_1)$ in $H_1$ (with color i) to the corresponding vertex of $M_i (G_2)$ in $H_2$ (with color i).
 
@@
 
-The results of the experiment are shown in Table \ref{table:results}.
+The results of the experiment are shown in table \ref{table:results}.
 Seven sets of graphs were tested for isomorphisms, and three cases the computation times are significantly different.
@@
 Due to the rather large difference in computation times relative to the preprocessing time, only significant differences in computation time will be used as indication of increase or decrease in speed.
+
+The preprocessing times for single graphs with $n$ nodes can be found in table \ref{table:results2}.
+These graphs contain no (false) twins, so these times are  only of the subroutine \emph{gettwins}.
+This is the extra computation time in case the preprocessing does nothing.
 
@@
 \end{multicols}
-\newpage
 \begin{appendices}
@@
 
-\section{Table with computation times}
-\begin{table}[h]
+\section{Tables with computation times}
+\begin{table}[h]\centering
 \begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
@@
 \end{table}
+\begin{table}[h]\centering
 
-\section{Complexity}
-\begin{table}[h]
 \begin{tabular}{c|c}
@@
 \end{tabular}
-\caption{Table showing the result from the experiment.
-For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
-\label{table:results}
+\caption{Table showing various preprocessing times, for graphs with $n$ nodes and no (false) twins.}
+\label{table:results2}
 \end{table}

### 2015-04-10 paper/paper.tex
proof
Fixed some things in paper

@@
 
-\noindent Abstract here
+This research paper shows how a certain preprocessing method, namely the finding and replacing of (false) twins, can be used to decrease the computation time on the graph isomorphism (GI) problem.
+The hypothesis of this study was that finding and replacing sets of (false) twins by a single node will decrease the computation time on finding isomorphisms between graphs.
+The paper also contains a mathematical prove which supports the claim that (false) twins can be replaced by a single node.
+During the project, an algorithm has been developed to find and replace these (false) twins.
+The algorithm computed different types of graphs with preprocessing both on and off.
+The results of these computational experiments have been compared and based on the differences in computation time a conclusion has been drawn.
+This conclusion is that it heavily depends on the type of graph: the more (false) twins a graph has, the faster a graph can be processed.
+The time of finding all the (false) twins can be neglected.
+The results also showed that for some graphs for which the GI problem cannot be solved without this preprocessing method, they could be solved with this preprocessing method.
 
@@
 
-This paper will discuss the effect of several preprocessing methods on the computation time of the graph isomorphism problem.
+This paper will discuss the effect of a certain preprocessing method on the computation time of the graph isomorphism problem.
 This paper will mostly focus on the algorithms and their correctness, in combination with computational experiments and their results.
@@
 The graph isomorphism problem is the computational problem of determining whether two finite graphs are isomorphic.
-Besides its practical importance, the graph isomorphism problem is a curiosity in computational complexity theory as it is one of a very small number of problems belonging to NP neither known to be solvable in polynomial time nor NP-complete: it is one of only 12 such problems listed by Garey \& Johnson (1979)\cite{book:garyJohnson1979}, and one of only two of that list whose complexity remains unresolved.
+Besides its practical importance, the graph isomorphism problem is a curiosity in computational complexity theory as it is one of a very small number of problems belonging to NP neither known to be solvable in polynomial time nor NP-complete: it is one of only 12 such problems listed by Garey \& Johnson (1979)\cite{book:garyJohnson1979}, and one of only two on that list whose complexity remains unresolved.
 As of 2008 the best algorithm (Eugene Luks, 1983) has run time $2^{O(\sqrt{n log n})}$ for graphs with \emph{n} vertices.\cite{article:davidJohnson2005}\cite{inproceedings:babaiCodenotti2008}\cite{website:wikiGI}
 
-The preprocessing part are algorithms that look at the graphs before determining whether they are isomorphic with the intent of finding some characteristic that might be used to speed up the actual process of the determining whether the graphs are isomorphic.
+The preprocessing part consists of algorithms that look at the graphs before determining whether they are isomorphic with the intent of finding some characteristic that might be used to speed up the actual process of the determining whether the graphs are isomorphic.
 
@@
 
-The aim of this research paper is to determine whether certain preprocessing methods significantly reduce the time required to check whether two graphs are isomorphic.
-At the core, two cases will be compared: a basic case without preprocessing, and a case with preprocessing.
+The aim of this research paper is to determine whether a certain preprocessing method significantly reduces the time required to check whether two graphs are isomorphic.
+At the core, two cases will be compared: a basic case without preprocessing and a case with preprocessing.
 
@@
 In both cases a timer was added to the code.
-The timer started before any other piece of code, and ended only after the algorithms were completely finished.
-This way everything is timed, including the loading of the graph, the additional time used to run preprocessing algorithms and finding of the isomorphisms.
+The timer started before any other piece of code and ended after the algorithms were completely finished.
+This way all the required computation is timed, including the loading of the graph, the additional time used to run preprocessing algorithms and the finding of isomorphisms.
 
-For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared.
+For every chosen test instance, the run time of both algorithms was determined. After all instances were computed, the results were compared.
 
@@
 \section{Description of Algorithms}
-For hard instances of the graph isomorphism problem, the coarsest stable coloring of a graph still has a lot of colors which are not unique.
+For hard instances of the graph isomorphism problem, the coarsest stable coloring of a graph still has colors which are not unique.
 Two structures for which this is the case are twins and false twins, they are defined in definition \ref{deftwins} and \ref{deffalsetwins}.
@@
 
-To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
+To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms to replace twins and false twins by single precolored vertices such that:
 \begin{compactenum}
 \item Vertices in the new graph have the same color $\iff$ The corresponding twinsets or false twinsets in the old graph have the same size (number of vertices).
-\item Two vertices in the new graph can't have the same color if one of them corresponds to a twinset and the other one two a false twinset in the old graph.
+\item Two vertices in the new graph cannot have the same color if one of them corresponds to a twinset and the other one two a false twinset in the old graph.
 \end{compactenum}
@@
 The elementary operation is the comparison of two elements.
-In those subsections $n$ is the number of vertices of a graph $G(V,E)$ and $m$ is the number of edges of that graph.
+In those subsections $n$ is the number of vertices of graph $G = (V,E)$ and $m$  the number of edges of graph $G$.
 
@@
 In the former list each sublist contains all the neighbours of a node and in the latter each sublist contains all the neighbours of a node and also the node itself.
-Finding all the neighbours only require going though all the edges once, so the time complexity is $O(m)$.
-The sorting algorithm has time complexity $O(y \log y)$, $y=$max(len($x$)), $x \in $ \emph{nbs} < $O(n \log n)$, but since it's in a for loop of length $n$ the overall time complexity becomes at most $O(n^2 \log n)$.
+Finding all the neighbours only requires going though all the edges once, so the time complexity is $O(m)$.
+The sorting algorithm has time complexity $O(y \log y)$, $y=$max(len($x$)), $x \in $ \emph{nbs} < $O(n \log n)$, but since it is in a for loop of length $n$ the overall time complexity becomes at most $O(n^2 \log n)$.
 
-In line 11-16 a dictionary \emph{falsetwins} is created where the keys are all the items from \emph{nbs} and the values a list of the corresponding vertices.
-The worst case time complexity of checking if an item is in a dictionary is $O(k+l)$ where $k$ is the number of keys and $l$ the length of the key which is a tuple.
-The average case is however only $O(l)$ \cite{website:pythonTimeComplexity}.
+In line 11-16 a dictionary \emph{falsetwins} is created where the keys are all the items from \emph{nbs} and the values are lists of the corresponding vertices.
+The worst case time complexity of checking if an item is in a dictionary is $O(k+l)$ where $k$ is the number of keys and $l$ the length of the key, which is a tuple.
+However, the average case is only $O(l)$ \cite{website:pythonTimeComplexity}.
 $l\leq n$ and $k\leq n$, and this dictionary operation is in a for loop of length $n$, so the worst case time complexity of this is $O(n^3)$, but the average case is $O(n^2)$.
@@
 \subsubsection{Replacing the twins}
-The algorithm \emph{preprocessing} can be found in appendix \ref{preprocessing}.
-In line 2 the twins and falsetwins are defined and if there are none the program will terminate.
-If there are any twins all edges with a head or tail in one of these twins will be deleted.
+The subroutine \emph{preprocessing} can be found in appendix \ref{preprocessing}.
+In line 2 the twins and falsetwins are defined and if there are none, the program will terminate.
+If there are any twins, all edges with a head or tail in one of these twins will be deleted.
 The complexity of this is $O(mv) < O (nm)$, where $v$ is the number of vertices in (\emph{twins}+\emph{falsetwins}).
@@
 Let $G_1 = (V_{G1}, E_{G1})$ and $G_2 = (V_{G2}, E_{G2})$ be two undirected  graphs and let $H_1 = (V_{H1}, E_{H1})$ and $H_2 = (V_{H2}, E_{H2})$ be resp.
-the same graphs as $G_1$ and $G_2$ where vertices which aren't (false) twins with any other vertex get color 0 and each (false) twin is replaced by a colored vertex such that: \begin{compactenum}[\upshape(a)]
+the same graphs as $G_1$ and $G_2$ where vertices which are not (false) twins with any other vertex get color 0 and each (false) twin is replaced by a colored vertex such that: \begin{compactenum}[\upshape(a)]
 \item Vertices in $H_1$ ($H_2$) have the same color $\iff$ The corresponding twinsets or false twinsets in $G_1$ ($G_2$) have the same size (number of vertices).
-\item Two vertices in $H_1$ ($H_2$) can't have the same color if one of them corresponds to a twinset in $G_1$ ($G_2$) and the other one corresponds to a false twinset in $G_1$ ($G_2$).
-They also can't have color 0.
+\item Two vertices in $H_1$ ($H_2$) cannot have the same color if one of them corresponds to a twinset in $G_1$ ($G_2$) and the other one corresponds to a false twinset in $G_1$ ($G_2$).
+They also cannot have color 0.
 \end{compactenum}
@@
 In the first case $g$ maps each $x \in$ \emph{ftw} to a different $y \in$ \emph{ftw2}.
-Since they are false twins it doesn't matter which $x$ is mapped to which $y$.
+Since they are false twins it does not matter which $x$ is mapped to which $y$.
 In the second case $g$ maps $x \in$ \emph{tw} to $y \in$ \emph{tw2} similarly.
@@
 The results of the experiment are shown in table \ref{table:results}.
-Seven sets of graphs were tested for isomorphisms, and three cases the computation times are significantly different.
+Seven sets of graphs were tested for isomorphisms and in three cases the computation time was significantly different.
 In the other cases, the preprocessing time is relatively very small.
 This is because the low complexity of \emph{gettwins} and the fact that \emph{preprocessing} does nothing when there are no (false) twins.
-The difference in computation time is not obviously related to the preprocessing time, as the preprocessing time is not equal to the difference in computation times.
-This is most likely due to the circumstances of both executions of the algorithms did not occur under the exact same circumstances, as it was impossible to ensure the conditions were the same.
+The difference in computation time is not related to the preprocessing time, as the preprocessing time is not equal to the difference in computation times.
+This is likely due to the circumstances of both executions of the algorithms not occurring under the exact same circumstances, as it was impossible to ensure the conditions were the same.
 
-Due to the rather large difference in computation times relative to the preprocessing time, only significant differences in computation time will be used as indication of increase or decrease in speed.
+Due to the large differences in computation times relative to the preprocessing time, only significant differences in computation time will be used as indication of increase or decrease in speed.
 
@@
 
-In three of the seven test cases, the computation time increased significantly. In the other four, no significant difference in the computation times was found.
+In three of the seven test cases the computation time increased significantly. In the other four there was no significant difference in the computation times.
 
-From this, it can be concluded that using preprocessing methods does indeed reduce the computation time needed to find graph isomorphisms.
+Thus, it can be concluded that this preprocessing method reduces the computation time needed to find isomorphisms between graphs that have (false) twins.
 

### 2015-04-10 paper/paper.tex
1 kleine verandering

@@
 The timer started before any other piece of code and ended after the algorithms were completely finished.
-This way all the required computation is timed, including the loading of the graph, the additional time used to run preprocessing algorithms and the finding of isomorphisms.
+This way all the required computations are timed, including the loading of the graph, the additional time used to run preprocessing algorithms and the finding of isomorphisms.
 

### 2015-04-10 paper/paper.tex
Fixed some things in paper

@@
 The graph isomorphism problem is the computational problem of determining whether two finite graphs are isomorphic.
-Besides its practical importance, the graph isomorphism problem is a curiosity in computational complexity theory as it is one of a very small number of problems belonging to NP neither known to be solvable in polynomial time nor NP-complete: it is one of only 12 such problems listed by Garey \& Johnson (1979)\cite{book:garyJohnson1979}, and one of only two on that list whose complexity remains unresolved.
+Besides its practical importance, the graph isomorphism problem is a curiosity in computational complexity theory as it is one of the few problems belonging to NP neither known to be solvable in polynomial time nor NP-complete: it is one of only 12 such problems listed by Garey \& Johnson (1979)\cite{book:garyJohnson1979}, and one of only two on that list whose complexity remains unresolved.
 As of 2008 the best algorithm (Eugene Luks, 1983) has run time $2^{O(\sqrt{n log n})}$ for graphs with \emph{n} vertices.\cite{article:davidJohnson2005}\cite{inproceedings:babaiCodenotti2008}\cite{website:wikiGI}
@@
 The results of the experiment are shown in table \ref{table:results}.
-Seven sets of graphs were tested for isomorphisms and in three cases the computation time was significantly different.
-In the other cases, the preprocessing time is relatively very small.
+Seven sets of graphs were tested for isomorphisms and in three cases the computation time was significantly shorter.
+In the other cases, the preprocessing time is relatively short compared to the total computing time.
 This is because the low complexity of \emph{gettwins} and the fact that \emph{preprocessing} does nothing when there are no (false) twins.

### 2015-04-10 paper/paper.tex
1 kleine verandering

@@
 This research paper shows how a certain preprocessing method, namely the finding and replacing of (false) twins, can be used to decrease the computation time on the graph isomorphism (GI) problem.
-The hypothesis of this study was that finding and replacing sets of (false) twins by a single node will decrease the computation time on finding isomorphisms between graphs.
-The paper also contains a mathematical prove which supports the claim that (false) twins can be replaced by a single node.
+The hypothesis of this study was that finding and replacing sets of (false) twins by a single colored node will decrease the computation time on finding isomorphisms between graphs.
+The paper also contains a mathematical proof which supports the claim that (false) twins can be replaced by a single colored node.
 During the project, an algorithm has been developed to find and replace these (false) twins.
@@
 The time of finding all the (false) twins can be neglected.
-The results also showed that for some graphs for which the GI problem cannot be solved without this preprocessing method, they could be solved with this preprocessing method.
+The results also showed that for some graphs for which the GI problem cannot be solved in reasonable time without this preprocessing method, they could be solved with this preprocessing method.
 
